---
title: "Value Added in Agrifood Systems - Step 3: UNIDO Manufacturing sector 2-digit ISIC code level value added data"
author: "Kate Schneider"
date: "`r Sys.Date()`"
output: html_document
bibliography: "Agrifood Value Added.bib"
---
#### Summary of Script 3

This script imports and cleans the data available at a more granular disaggregation for the Manufacturing Main Aggregate from UNIDO. We manually downloaded the ISIC Revision 3 data at the 2-digit level in January 2024 and they are saved in the "UNIDO INDSTAT2 ISIC Rev 3_15Jan2024" subfolder under "Input Data". We manually downloaded the ISIC Revision 4 data only available at the 4-digit level in January 2024 and they are saved in the "UNIDO INDSTAT4 ISIC Rev4_6Jan2024" subfolder under "Input Data". The date in the subfolder names indicates the download date. These data disaggregate the Manufacturing Aggregate, which is "D" in ISIC Revision 3 and "C" in ISIC Revision 4.

*Tables imported:*

-   INDSTAT 2, ISIC Revision 3: All countries and years, Value Added statistic in national currency from <https://stat.unido.org/content/dataset_description/indstat-2-2023%252c-isic-revision-3>
-   INDSTAT 4, ISIC Revision 4: All countries and years from 1995 forward, Value Added statistic in national currency from: <https://stat.unido.org/database/INDSTAT%204%202023,%20ISIC%20Revision%204>

The INDSTAT2 database harmonizes historical and new data to the ISIC Revision 3. Concordance tables are available at:

-   Broad correspondence: <https://unece.org/fileadmin/DAM/stats/documents/ece/ces/ge.20/2006/mtg2/zip.8.e.pdf>
-   4-digit level: <https://www.unescwa.org/sites/default/files/event/materials/event_detail_id_681_tablesbtwnisicrev.pdf>

Finally, note that while there is a complete documentation User's Guide for INDSTAT2 (available for ISIC Rev 3 only), there is no such documentation for INDSTAT4 for either ISIC revision. The only documentation available is at the following site: <https://stat.unido.org/content/dataset_description/indstat-4-2023%252c-isic-revision-4>

```{r setup, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
### Setup required to knit this script into a markdown document

    # Load the knitr package
      library(knitr)
    
    # Set echo = FALSE for all code chunks will prevent the code from printing in the output file
      knitr::opts_chunk$set(echo = FALSE)
      
# Set the root folder to the project root so that all file paths are relative to the main project folder
    knitr::opts_knit$set('./')
  
# Set the treatment of numbers to numerical (avoids scientific notation from showing in results)
    options(scipen = 999)

# Load packages
    # R studio should prompt the installation of any packages not loaded on the instance where this script has been opened
    library(tidyverse)
    library(Hmisc)
    library(haven)
    library(readxl)
    library(labelled)
    library(data.table)
    library(psych)
    library(kableExtra)
    library(citr) ## To install from github: devtools::install_github("crsh/citr")
    library(testthat)
    library(pals)
    library(here)

# Set relative directory paths
    data_in <- here::here("Input Data")
    fig_out <- here::here("Figures")
    support <- here::here("Support files and scripts")
    data_out <- here::here("Output Datasets")

# Create a "not in" operator
    `%notin%` <- Negate(`%in%`) 
    
# Create a function to test that there are  no duplicates in the data frame
    isUnique <- function(vector){
           return(!any(duplicated(vector)))
    }
    
# Note: "$~$" adds line breaks in the html report in the knitting process.
```

$~$

### *Input data set 4: UNIDO Manufacturing Sector Data*

We start with ISIC Revision 3.
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}

# Import the UNIDO Data
    inst.classes <- c("factor","factor","factor","factor","factor","numeric","factor","factor","factor")
    inst.names  <- c("ctable","country","year","isic","isiccomb","value","utable","source","unit")
    inst        <- read.csv(file= file.path(data_in, "UNIDO INDSTAT2 ISIC Rev 3_15Jan2024/data.csv"), header=FALSE, col.names=inst.names, colClasses=inst.classes, na.strings="...")
    
    my_labels <- c(
      ctable = "Table Code",
      country = "Country Code",
      year = "Year",
      isic = "ISIC Code", # 2-digit code within manufacturing aggregate "D"
      isiccomb = "ISIC Combination Code", # Indicates countries reporting only an aggregate of multiple 2-digit codes
      value = "Value",
      utable = "Table Definition code",
      source = "Source Code",
      unit = "Unit"
    )
    
    listoflabels <- as.list(my_labels[match(names(inst), names(my_labels))])

# Filter for the Value Added table
    ManufVA_Rev3 <- inst %>% filter(ctable == 20) 

# Filter the years included in this study
    ManufVA_Rev3 <- ManufVA_Rev3 %>% filter(year %in% 1995:2021) 

# Merge with geographic information
    levels(ManufVA_Rev3$country)
    ManufVA_Rev3 <- ManufVA_Rev3 %>% rename(m49_code = country)
    ManufVA_Rev3 <- ManufVA_Rev3 %>% mutate(m49_code = as.character(m49_code))
    
# Open area info data frame created in Script #1
    load(file.path(data_in, "Area_info.Rdata"))

# Join area info with manufacturing data
    Area_info <- Area_info %>% mutate(m49_code = as.character(m49_code))
    ManufVA_Rev3 <- left_join(ManufVA_Rev3, Area_info, by = "m49_code") %>% 
      select(-c(1,7:9,13:20))
    ManufVA_Rev3 <- ManufVA_Rev3 %>% mutate(isic = as.character(isic))

# Note that there is negative value added. This has been confirmed on the UNIDO database as correctly importing from the official statistics
    ManufVA_Rev3 <- ManufVA_Rev3 %>% mutate(value = as.numeric(value))
    range(ManufVA_Rev3$value, na.rm = TRUE)
    
    # M49 codes that do not match with area info
    ManufVA_Rev3 %>% filter(is.na(country)) %>% distinct(m49_code)
        # Codes no longer in use: 736 = former Sudan, 412 = Kosovo, 530 = former Netherlands Antilles, 891 = former Serbia and Montenegro
    ManufVA_Rev3 <- ManufVA_Rev3 %>% 
      filter(!(is.na(country)))
    
    isUnique(ManufVA_Rev3)

# Clean up
    rm(inst, inst.classes, inst.names)

```

$~$

UNIDO data contain 2-digit level information for ISIC codes under the main aggregate category of "D". However, some countries report aggregated values that contain a combination of 2-digit level categories (Annex III in [@unidoINDSTAT22020ISIC2020]). We converted the ANNEX III table from the PDF file into a digital file, saved in (and called from in the code) the "INDSTAT_ISICComboCodes.Rdata" data frame in the "Support files and scripts" project subfolder. We do not have any approach to disaggregate these codes, we hereby document them as a limitation of the data.
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# Merge the combination codes with the UNIDO data
    load(file.path(support, "INDSTAT_ISICComboCodes.RData"))
    ComboCodes <- table # rename the data frame
      rm(table)
    class(ComboCodes$isiccomb)
    class(ManufVA_Rev3$isiccomb)
    ManufVA_Rev3 <- ManufVA_Rev3 %>% mutate(isiccomb = as.character(isiccomb))
    ManufVA_Rev3 <- left_join(ManufVA_Rev3, ComboCodes, by = "isiccomb")

# Merge classification to AFS
    # Open ISIC Rev 3 data frame created in Script #1
        load(file.path(data_in, "ISICRev3.Rdata"))
    
# Merge classification with manufacturing data
    Manuf_ISIC_Rev3 <- ISICRev3 %>% filter(row_number() %in% c(51:263)) %>%
      rename("isic" = "Code")
    ManufVA_Rev3 <- left_join(ManufVA_Rev3, Manuf_ISIC_Rev3, by = c("isic")) %>%
      select(-c(12:16)) %>%
      rename(ISIC_Item = "Item",
             Year = "year")

# Add columns present in AgriFood_sum so this data frame can be appended
    # Open Agrifood_sum_Rev3 created in Script #2
        load(file.path(data_in, "AgriFood_sum_Rev3.Rdata"))
        isUnique(AgriFood_sum_Rev3)
        
    # Join
        AFScols <- AgriFood_sum_Rev3 %>% select(c("ISO", "Year", "Currency")) %>%
          unique() %>%
          filter(!(is.na(ISO))) %>%
          mutate(Year = as.factor(Year))
        ManufVA_Rev3 <- left_join(ManufVA_Rev3, AFScols, by = c("ISO", "Year"))
        isUnique(ManufVA_Rev3)

# Remove main aggregate because all the 2-digit codes sum to the main aggregate
    ManufVA_Rev3 <- ManufVA_Rev3 %>%
      filter(isic != "D") %>%
      # Make sure the country names are correct
          mutate(country = case_when(country == "Venezuela, Bolivarian Republic of" ~ "Venezuela (Bolivarian Republic of)",
                               country == "Côte D'Ivoire" ~ "Côte d'Ivoire",
                               country == "Netherlands" ~ "Netherlands (Kingdom of the)",
                               TRUE ~ country))
  isUnique(ManufVA_Rev3)
  
# Save data frame 
    save(ManufVA_Rev3, file = file.path(data_in, "ManufVA_Rev3.RData"))
```

$~$

**Table 1. Classification and description of combined 2-digit categories reported by some countries in INDSTAT2 data - ISIC Rev 3**
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Table of combination codes and description for inspection
    descriptions <- ManufVA_Rev3 %>% select(isiccomb, isic, ISIC_Item, Is_AFS)
    inspect_combo <- left_join(ComboCodes, descriptions, by = "isiccomb") %>%
      group_by(isic) %>% filter(row_number() == 1) %>%
      filter(!is.na(Is_AFS))

# Clean up
    rm(descriptions)
    
# Create table to show combination codes
    kable(inspect_combo, col.names = c("Combination Code", "Combined Categories", "Classified under", "Description", "Is AFS? (1=yes, 2=partial, 0=No"), format = "html", caption = "Classification and description of combined 2-digit categories reported by some countries in INDSTAT2 data") %>% kable_classic(full_width = T, html_font = "Cambria")

# Clean up
    rm(descriptions, inspect_combo)
```

$~$

We repeat with ISIC Revision 4.
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# Import the UNIDO Data
    inst.classes <- c("factor","factor","factor","factor","factor","numeric","factor","factor","factor")
    inst.names <- c("ctable","country","year","isic","isiccomb","value","utable","source","unit")
    inst <- read.csv(file = file.path(data_in, "UNIDO INDSTAT4 ISIC Rev 4_6Jan2024/data.csv"), header=FALSE, col.names=inst.names, colClasses=inst.classes, na.strings="...")
    
    my_labels <- c(
      ctable = "Table Code",
      country = "Country Code",
      year = "Year",
      isic = "ISIC Code", # 2-digit code within manufacturing aggregate "D"
      isiccomb = "ISIC Combination Code", # Indicates countries reporting only an aggregate of multiple 2-digit codes
      value = "Value",
      utable = "Table Definition code",
      source = "Source Code",
      unit = "Unit"
    )
    
    labellist <- as.list(my_labels[match(names(inst), names(my_labels))])
    
# Filter for the Value Added table if other variables have been downloaded
    ManufVA_Rev4 <- inst %>% filter(ctable == 20) 

# Merge with geographic information
    levels(ManufVA_Rev4$country)
    ManufVA_Rev4 <- ManufVA_Rev4 %>% rename(m49_code = country)
    ManufVA_Rev4 <- ManufVA_Rev4 %>% mutate(m49_code = as.character(m49_code))
    ManufVA_Rev4 <- left_join(ManufVA_Rev4, Area_info, by = "m49_code") %>% select(-c(1,7:9,13:20))
    ManufVA_Rev4 <- ManufVA_Rev4 %>% mutate(isic = as.character(isic))

    # M49 codes that do not match with area info
    ManufVA_Rev4 %>% filter(is.na(country)) %>% distinct(m49_code)
        # Code 412 = Kosovo
    ManufVA_Rev4 <- ManufVA_Rev4 %>% 
      filter(!(is.na(country)))

    
# Clean up
    rm(inst, inst.classes, inst.names)
```

$~$

With the ISIC Revision 4 data, we have an additional challenge of interpreting the combined codes due to the lack of full documentation. We cannot use the INDSTAT User's Guide Annex III [@unidoINDSTAT22020ISIC2020] information because it does not contain the combination codes used in the INDSTAT4 database. Again, we have no method to disaggregate these codes but note the additional limitation here that we also do not have documentation of the categories we are unable to use in the analysis.
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# The following code demonstrates that we cannot use the combination codes from the INDSTAT2 documentation with the UNIDO INDSTAT4 data because the INDSTAT4 combination codes are not contained in that Annex documentation. 
  # ManufVA_Rev4 <- ManufVA_Rev4 %>% mutate(isiccomb = as.character(isiccomb))
  # ManufVA_Rev4 <- left_join(ManufVA_Rev4, ComboCodes, by = "isiccomb") # No matches when joining the data

# Merge classification to AFS
    # Open ISIC Rev 4 data frame created in Script #1
        load(file.path(data_in, "ISICRev4.Rdata"))

    # Join
        Manuf_ISIC_Rev4 <- ISICRev4 %>% filter(row_number() %in% c(86:318)) %>%
          rename("isic" = "Code")
        ManufVA_Rev4 <- left_join(ManufVA_Rev4, Manuf_ISIC_Rev4, by = c("isic")) %>%
          select(-c(12:16)) %>%
          rename(ISIC_Item = "Item",
                 Year = "year") 

# Add columns present in AgriFood_sum so this dataframe can be appended
    # Open Agrifood_sum data frame created in Script #2
        load(file.path(data_in, "AgriFood_sum_Rev4.Rdata"))
    
    #
        AFScols <- AgriFood_sum_Rev4 %>% select(c("ISO", "Currency")) %>%
          unique()
        ManufVA_Rev4 <- left_join(ManufVA_Rev4, AFScols, by = c("ISO"))

# Filter out rows with no value added recorded
    ManufVA_Rev4 <- ManufVA_Rev4 %>% filter(!(is.na(value)))
    
# Save data frame 
    save(ManufVA_Rev4, file = file.path(data_in, "ManufVA_Rev4.RData"))

# Now we want to remove the main aggregate and all the 4-digit level data because the 4-digit codes present sum up to the 3-digit codes. Some countries do not report all categories at the 4-digit level and some countries do not report all the 3-digit level codes and only report 4-digits. So we first have to ensure that all the 3-digit codes are present.
    
    # First we fill in the missing codes
      df1 <- ManufVA_Rev4 %>%
        select(c(country, Year)) %>% unique()
      df2 <- Manuf_ISIC_Rev4 %>% select(-c(Justification))
      completed <- crossing(df1,df2)
      # show which country-code-year combinations were not present in the dataset:
        codestofillin <- anti_join(completed, ManufVA_Rev4, by = c("country", "Year", "isic"))
    
    # Now that we've found the missing combinations of country-year-code, we merge those into the dataset
      df1 <- ManufVA_Rev4 %>%
        select(c("m49_code", "country", "ISO", "UNmemberstate")) %>%
        unique()
      codestofillin <- left_join(codestofillin, df1, by = c("country")) %>%
        select(-c("Filter_2", "Filter_3", "Filter_4", "HasData")) %>%
        mutate(isiccomb = "",
               value = NA,
               Currency = "") %>%
        rename(ISIC_Item = Item)
      codestofillin <- codestofillin[, names(ManufVA_Rev4)]
      # Now add the missing rows to the main dataset
        ManufVA_Rev4 <- rbind(ManufVA_Rev4, codestofillin)
        ManufVA_Rev4 <- ManufVA_Rev4 %>%
          arrange(country, Year, isic) %>%
          # Create a flag for the added rows
          mutate(flag = case_when(Currency == "" ~ 1,
                                TRUE ~ 0)) 
    
        # Use the ISIC Codes data set to construct the linkage for summation
        # First we sum (or carry) 4-digit codes to the 3 digit level
            ISICRev4_manuf <- ISICRev4[86:326,] %>%
              mutate(sum_to = paste(Code.1, Code.2, Code.3, sep = ""),
                     sum_to = as.numeric(sum_to)) %>%
              rename(isic = Code,
                     ISIC_Item = Item) %>%
              filter(Filter_3 !=1) %>%
              # Now remove the main aggregate and 1-digit level codes
              filter(Filter_1 !=1,
                     Filter_2 !=1) %>%
              select(1,2,14)
         
  # Merge the sum_to instruction into the manufacturing data frame
      ManufVA_Rev4 <- left_join(ManufVA_Rev4, ISICRev4_manuf, by = c("isic", "ISIC_Item")) %>%
        arrange(country, Year) %>%
      # Make sure the country names are correct
          mutate(country = case_when(country == "Venezuela, Bolivarian Republic of" ~ "Venezuela (Bolivarian Republic of)",
                               country == "Côte D'Ivoire" ~ "Côte d'Ivoire",
                               country == "Netherlands" ~ "Netherlands (Kingdom of the)",
                               TRUE ~ country))
  
  # Aggregate by country, year, sum_to
      Rev4_to3digitsfrom4 <- ManufVA_Rev4 %>%
        filter(!(is.na(Code.4))) %>%
        group_by(country, Year, sum_to) %>%
        aggregate(value ~ country + Year + sum_to, FUN = sum, na.rm = TRUE) %>%
        rename(recalculated_value = value) %>%
        mutate(isic = as.character(sum_to)) %>%
        select(-c(sum_to))
      ManufVA_Rev4 <- left_join(ManufVA_Rev4, Rev4_to3digitsfrom4, by = c("country", "Year", "isic"))
      
      # First, test whether the 3-dig code equals the summed up 4-digits where the 3-digit code was present in the data
      test <- ManufVA_Rev4 %>%
        filter(!(is.na(Code.3)) & !(is.na(recalculated_value))) %>%
        mutate(bigger3dig = case_when(value > recalculated_value ~ 1, TRUE ~ 0),
               equal = case_when(value == recalculated_value ~ 1, TRUE ~ 0),
               smaller3dig = case_when(value < recalculated_value ~ 1, TRUE ~ 0))
      rm(test)
      
      # Now replace any missing 3-digit code data with the newly calculated or carried over value
      # Or any 3-digit code that is smaller than the sum of the subordinate categories
      ManufVA_Rev4 <- ManufVA_Rev4 %>%
        mutate(value = case_when(is.na(value) ~ recalculated_value,
                                 value < recalculated_value ~ recalculated_value,
                                 TRUE ~ value)) %>%
        select(-c(sum_to))
      
    # Now we remove all the 4-digit level data
      ManufVA_Rev4 <- ManufVA_Rev4 %>%
        rename(four_dig_ID = "Code.4") %>%
        filter(is.na(four_dig_ID)) %>%
        filter(isic != "C") %>%
        select(-c(four_dig_ID, recalculated_value)) 
    # Test for no duplicates 
        isUnique(ManufVA_Rev4)

# Now we aggregate the 3-digit level data to their 2-digit supra-ordinate categories so that it can be combined and visualized with the country-years for which we only have the 2-digit level ISIC Revision 3 data for the manufacturing sector
  
    # Again use the ISIC Codes data set to construct the linkage for summation
        # Remove codes outside manufacturing and 3-digit level codes
            ISICRev4_manuf <- ISICRev4[86:326,] %>%
              mutate(sum_to = paste(Code.1, Code.2, sep = ""),
                     sum_to = as.numeric(sum_to)) %>%
              rename(isic = Code,
                     ISIC_Item = Item) %>%
              filter(Filter_4 !=1) %>%
              # Now remove the main aggregate and 1-digit level codes
              filter(Filter_1 !=1,
                     Filter_2 !=1) %>%
              select(1,2,14)
         
  # Merge the sum_to instruction into the manufacturing data frame
      ManufVA_Rev4 <- left_join(ManufVA_Rev4, ISICRev4_manuf, by = c("isic", "ISIC_Item")) %>%
        arrange(country, Year) %>%
      # Make sure the country names are correct
          mutate(country = case_when(country == "Venezuela, Bolivarian Republic of" ~ "Venezuela (Bolivarian Republic of)",
                               country == "Côte D'Ivoire" ~ "Côte d'Ivoire",
                               country == "Netherlands" ~ "Netherlands (Kingdom of the)",
                               TRUE ~ country))
  
  # Aggregate by country, year, sum_to
      Rev4_to2digitsfrom3 <- ManufVA_Rev4 %>%
        group_by(country, Year, sum_to) %>%
        aggregate(value ~ country + Year + sum_to, FUN = sum) %>%
        rename(isic = sum_to)%>%
        rename(recalculated_value = value) %>%
        mutate(isic = as.character(isic))
      ManufVA_Rev4 <- left_join(ManufVA_Rev4, Rev4_to2digitsfrom3, by = c("country", "Year", "isic"))
      
    # Now replace any missing 2-digit code data with the newly calculated or carried over value
      ManufVA_Rev4 <- ManufVA_Rev4 %>%
        mutate(value = recalculated_value)
      
    # Now we remove all the 3-digit level data
      ManufVA_Rev4_aggregate <- ManufVA_Rev4 %>%
        rename(three_dig_ID = "Code.3") %>%
        filter(is.na(three_dig_ID)) %>%
        filter(isic != "C") %>%
        select(-c(three_dig_ID, sum_to, recalculated_value, Currency, flag))
        # Test for no duplicates 
        isUnique(ManufVA_Rev4_aggregate)
        
    # Filter out the country-year records for China that show in the dataset but had no data under the manufacturing main aggregate (C)
      ManufVA_Rev4_aggregate <- ManufVA_Rev4_aggregate %>%
        filter(!(is.na(value)))
   
# Now merge back in the rest of the variables
    # ISIC Classification columns
    ManufVA_Rev4_aggregate <- ManufVA_Rev4_aggregate %>% select(-c(4, 10:13)) %>%
      rename(Code = isic)
    ManufVA_Rev4_aggregate <- left_join(ManufVA_Rev4_aggregate, select(ISICRev4[86:326,], c(1,3,9:13)), by = "Code") %>%
      # Make sure the country names are correct
          mutate(country = case_when(country == "Venezuela, Bolivarian Republic of" ~ "Venezuela (Bolivarian Republic of)",
                               country == "Côte D'Ivoire" ~ "Côte d'Ivoire",
                               country == "Netherlands" ~ "Netherlands (Kingdom of the)",
                               TRUE ~ country))
    # Add currency
      load(file.path(data_in, "ManufVA_Rev4.Rdata"))
      currency <- ManufVA_Rev4 %>% select(2,6,16) %>% unique()
      ManufVA_Rev4_aggregate <- left_join(ManufVA_Rev4_aggregate, currency, by = c("Year", "country"))

# Save data frame 
    save(ManufVA_Rev4_aggregate, file = file.path(data_in, "ManufVA_Rev4_aggregate.RData"))
```

$~$

**Table 2. Classification and description of combined 3-digit categories reported by some countries in INDSTAT4 data - ISIC Rev 4**
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Table of combination codes and description for inspection
    descriptions <- ManufVA_Rev4 %>% select(isiccomb, isic, ISIC_Item, Is_AFS)
    inspect_combo <- descriptions %>%
      group_by(isic) %>% filter(row_number() == 1) %>%
      filter(!is.na(Is_AFS))

# Create table to show combination codes
    kable(inspect_combo, col.names = c("Combination Code", "Classified under", "Description", "Is AFS? (1=yes, 2=partial, 0=No"), format = "html", caption = "Classification and description of combined 3- and 4-digit categories reported by some countries in INDSTAT4 ISIC Rev 4 data") %>% kable_classic(full_width = T, html_font = "Cambria")

# Clean up
    rm(inspect_combo, ComboCodes, descriptions)
  
```

$~$

**References**
