---
title: "Value Added in Agrifood Systems - Step 5: Merge datasets and create final output datasets"
author: "Kate Schneider"
date: "`r Sys.Date()`"
output: html_document
bibliography: "Agrifood Value Added.bib"
---
### *Summary of Script 5*

This script merges the data sets created in scripts #1 to #4 into a final time series data set of agrifood system value added.

```{r setup, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
### Setup required to knit this script into a markdown document

    # Load the knitr package
      library(knitr)
    
    # Set echo = FALSE for all code chunks will prevent the code from printing in the output file
      knitr::opts_chunk$set(echo = FALSE)
      
# Set the root folder to the project root so that all file paths are relative to the main project folder
    knitr::opts_knit$set('./')
  
# Set the treatment of numbers to numerical (avoids scientific notation from showing in results)
    options(scipen = 999)

# Load packages
    # R studio should prompt the installation of any packages not loaded on the instance where this script has been opened
    library(tidyverse)
    library(Hmisc)
    library(here)
    library(haven)
    library(readxl)
    library(labelled)
    library(data.table)
    library(psych)
    library(kableExtra)
    library(citr) ## To install from github: devtools::install_github("crsh/citr")
    library(testthat)
    library(pals)
    library(countrycode)

# Set relative directory paths
    data_in <- here::here("Input Data")
    fig_out <- here::here("Figures")
    support <- here::here("Support files and scripts")
    data_out <- here::here("Output Datasets")

# Create a "not in" operator
    `%notin%` <- Negate(`%in%`) 
    
# Create a function to test that there are  no duplicates in the data frame
    isUnique <- function(vector){
           return(!any(duplicated(vector)))
    }

# Note: "$~$" adds line breaks in the html report in the knitting process.
```

### Merge data sets

### Load datasets with the multiple series flag
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# Create data frame of countries with multiple time series and add a quality flag
    load(file = file.path(data_in, "multseries_latest3.RData"))
    load(file = file.path(data_in, "multseries_longestlatest3.RData"))
    load(file = file.path(data_in, "multseries_latest4.RData"))
    load(file = file.path(data_in, "multseries_longestlatest4.RData"))
    
    multseries_latest3$multseries_flag <- "Latest shorter"
    multseries_latest3$ISIC_Rev <- 3
    multseries_longestlatest3$multseries_flag <- "Latest=longest"
    multseries_longestlatest3$ISIC_Rev <- 3
    multseries_latest4$multseries_flag <- "Latest shorter"
    multseries_latest4$ISIC_Rev <- 4
    multseries_longestlatest4$multseries_flag <- "Latest=longest"
    multseries_longestlatest4$ISIC_Rev <- 4
    multseries_flag <- rbind(multseries_latest3, multseries_longestlatest3, multseries_latest4, multseries_longestlatest4) %>%
      arrange(country)
    isUnique(multseries_flag)
    # A few countries end up with duplicate rows because they have Rev 3 and Rev 4 data, delete the Rev 3 rows
      multseries_flag <- multseries_flag %>%
        mutate(dup_country = case_when(country == lead(country) & ISIC_Rev == 3 ~ 1,
                                       TRUE ~ 0)) %>%
        filter(dup_country == 0) %>% select(-c(dup_country))
    
    # Clean up
    rm(multseries_latest3, multseries_longestlatest3, multseries_latest4, multseries_longestlatest4)
```

#### ISIC Revision 4
We start with the data using ISIC Revision 4.

```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# First select the main aggregates data
    load(file = file.path(data_in, "AgriFood_sum_Rev4.RData"))
    isUnique(AgriFood_sum_Rev4)
    MainAggregates_Rev4 <- AgriFood_sum_Rev4 %>%
      filter(!(ISIC_Item == "Equals: GROSS DOMESTIC PRODUCT")) %>% # filter out GDP as a row, will be added later as a column from the GDP series
      select(c("country", "ISO", "m49_code", "Year", "ISIC_Item", "ValueAdded", "Is_AFS", "SNA93 Item Code")) %>%
      # Make sure the years are within the period of analysis 
      filter(Year <= 2021 & Year >= 1995)
    isUnique(MainAggregates_Rev4)

# Next select the manufacturing data (aggregated to the 2-digit level)
    load(file = file.path(data_in, "ManufVA_Rev4_aggregate.RData"))
    Manufacturing_Rev4 <- ManufVA_Rev4_aggregate %>%
      filter(Is_AFS != 0) %>% # filter out the non-AFS categories
      select(c("country", "ISO", "m49_code", "Year", "ISIC_Item", "value", "Is_AFS")) %>%
      rename(ValueAdded = value) %>%
      mutate(Year = as.character(Year)) %>%
      mutate(Year = as.numeric(Year)) 
    isUnique(Manufacturing_Rev4)

```

$~$

Identify countries with no Revision 4 manufacturing data in the UNIDO database.

**Table 1. Countries with no ISIC Rev 4 manufacturing sector disaggregated data in UNIDO database**
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Use anti-join for identification
    no_UNIDO_data_Rev4 <- anti_join(MainAggregates_Rev4[, c("country", "Year")], Manufacturing_Rev4[, c("country", "Year")], by = c("country", "Year")) %>% unique()

# Create table
    # kable(no_UNIDO_data_Rev4, "html", caption = "Countries with no ISIC Rev 4 manufacturing sector disaggregated data in UNIDO database") %>% 
    #   kable_classic(full_width = F, html_font = "Cambria")
```

$~$

Now remove manufacturing only for countries that HAVE the UNIDO data.
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# Now remove manufacturing only for countries that HAVE the UNIDO data
# Note that we will recreate an AFS only share of the total manufacturing main aggregate for these countries with the disaggregated UNIDO data for visualization later on in this script

# We use the country-year list from the anti-join step above to identify these country-years.
    no_UNIDO_data_Rev4$hasUNIDO <- 0 
    MainAggregates_Rev4 <- left_join(MainAggregates_Rev4, no_UNIDO_data_Rev4, 
                                     by = c("country", "Year")) %>%
      mutate(hasUNIDO = case_when(is.na(hasUNIDO) ~ 1,
                                   TRUE ~ hasUNIDO)) %>%
      # Now drop the manufacturing main aggregate only where there are UNIDO data (hasUNIDO == 1) and also the aggregate manufacturing category if that was retained instead
      filter(!((hasUNIDO == 1 & ISIC_Item == "Manufacturing") |
               (hasUNIDO == 1 & ISIC_Item == "Manufacturing, mining and quarrying and other industrial activities")))

# Now add the SNA93 Item Code variable to the manufacturing data set
    # This is important because the SNA93 Item Code variable is used when we merge ISIC Rev 3 and Rev 4 data
        Manufacturing_Rev4$"SNA93 Item Code" <- "C"
        
# Finally, we have to make sure we're not including manufacturing data for country-years that do not have main aggregates, so we repeat the anti-join. 
    no_SNA_data_Rev4 <- anti_join(Manufacturing_Rev4[, c("country", "Year")], MainAggregates_Rev4[, c("country", "Year")], by = c("country", "Year")) %>% unique()

# Create table
    kable(no_SNA_data_Rev4, "html", caption = "Countries with no ISIC Rev 4 SNA data but do have UNIDO manufacturing data - excluded from final dataset for lack of Main Aggregates") %>% 
      kable_classic(full_width = F, html_font = "Cambria")
    
    # Remove from manufacturing data frame
    no_SNA_data_Rev4$hasSNA <- 0 
    Manufacturing_Rev4 <- left_join(Manufacturing_Rev4, no_SNA_data_Rev4, 
                                     by = c("country", "Year")) %>%
      mutate(hasSNA = case_when(is.na(hasSNA) ~ 1,
                                   TRUE ~ hasSNA)) %>%
      filter(hasSNA == 1) 


# Now append the manufacturing data to the main aggregates data for the country-years with UNIDO data at the ISIC Rev 4 level
    MainAggregates_Rev4 <- MainAggregates_Rev4 %>% select(-c("hasUNIDO"))
    Manufacturing_Rev4 <- Manufacturing_Rev4 %>% select(-c("hasSNA"))
    AFSValAdded_Rev4 <- rbind(MainAggregates_Rev4, Manufacturing_Rev4) %>%
      arrange(country, Year)
    
  isUnique(AFSValAdded_Rev4)

```

$~$

**Table 2. ISIC Rev 4 Categories in Agrifood System at level where data are available**
Note this table repeats from Script #2.
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Rename the ISIC_Item values to match the fractions
    AFSValAdded_Rev4 %>% select(c("ISIC_Item")) %>%
      unique() %>% mutate(ISIC_Item = as.factor(ISIC_Item)) %>% 
      arrange(ISIC_Item) %>%
      kable("html", caption = "ISIC Rev 4 Categories in Agrifood System at level where data are available") %>% 
      kable_classic(full_width = F, html_font = "Cambria")
```

$~$

**Merge in the fractions and calculate AFS shares.**
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>% 
  mutate(fraction_name = case_when(str_detect(ISIC_Item, pattern = "(?i)mining") ~ "B_Mining",
                               ISIC_Item == "Manufacturing" ~ "C_AFSManuf",
                               str_detect(ISIC_Item, pattern = "(?i)textile") ~ "C13_Textiles",
                               str_detect(ISIC_Item, pattern = "(?i)wearing apparel") ~ "C14_WearingApparel",
                               str_detect(ISIC_Item, pattern = "(?i)leather") ~ "C15_Leather",
                               str_detect(ISIC_Item, pattern = "(?i)chemicals") ~ "C20_Chemicals", 
                               str_detect(ISIC_Item, pattern = "(?i)pharmaceuticals") ~ "C21_Pharma", 
                               str_detect(ISIC_Item, pattern = "(?i)rubber") ~ "C22_Rubber", 
                               str_detect(ISIC_Item, pattern = "(?i)machinery") ~ "C28_Machinery", 
                               str_detect(ISIC_Item, pattern = "(?i)furniture") ~ "C31_Furniture",
                               str_detect(ISIC_Item, pattern = "(?i)wholesale") ~ "G_Trade",
                               str_detect(ISIC_Item, pattern = "(?i)electricity") ~ "D_Electric",
                               str_detect(ISIC_Item, pattern = "(?i)water") ~ "E_Water",
                               str_detect(ISIC_Item, pattern = "(?i)retail") ~ "G_Trade",
                               str_detect(ISIC_Item, pattern = "(?i)accom") ~ "I_AccomFood",
                               str_detect(ISIC_Item, pattern = "(?i)transport") ~ "H_Transport",
                               str_detect(ISIC_Item, pattern = "(?i)professional") ~ "M_ProfSciTech",
                               str_detect(ISIC_Item, pattern = "(?i)public administration") ~ "O_PubAdmin",
                               Is_AFS == 1 ~ "1")) # Replace fraction = 1 for categories that are wholly AFS (Is_AFS = 1)

  # Now revise which fraction is used for B+C+D+E aggregate when nothing better is available - use the manufacturing fraction (code above would lead to mining as the fraction because it appears earlier in the code)
  AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
    mutate(fraction_name = case_when(ISIC_Item == "Manufacturing, mining and quarrying and other industrial activities" ~ "C_AFSManuf",
                                   TRUE ~ fraction_name)) 

# Now add the fractions
    load(file = file.path(data_in, "fractions_Rev4.Rdata"))
    AFSValAdded_Rev4 <- left_join(AFSValAdded_Rev4, fractions_Rev4, by = c("ISO", "Year", "fraction_name"))

# Replace fraction = 1 for wholly AFS 
    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
      mutate(fraction_val = case_when(Is_AFS == 1 ~ 1,
                                         TRUE ~ fraction_val))

# Add in the second fraction for disaggregating manufacturing
    C_AFSInputManuf <- fractions_Rev4 %>% filter(fraction_name == "C_AFSInputManuf") %>%
      rename(C_AFSInputManuf = fraction_val) %>% select(-c(fraction_name))
    AFSValAdded_Rev4 <- left_join(AFSValAdded_Rev4, C_AFSInputManuf, by = c('ISO', 'Year')) 

# Sum the AFS Manufacturing fractions so that the share of manufacturing attributed to AFS is the share of manufacturing of AFS production AND the share of manufacturing that is inputs into AFS production
    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
      mutate(fraction_val = case_when(ISIC_Item == "Manufacturing" ~ (fraction_val + C_AFSInputManuf), TRUE ~ fraction_val)) %>%
      select(-c("C_AFSInputManuf"))

# Create a flag variable to indicate which country-years have only 2 disaggregations for manufacturing (AFS-based products, AFS production inputs), which are in other words the country-years where we use the fraction method to disaggregate. This flag is important because no country-years will have data for the estimated disaggregations if it had data in the UNIDO data base and vice versa, so we will need to accommodate for this in the visualizations if combining across the estimated and observed manufacturing disaggregates. 
    flag <- AFSValAdded_Rev4 %>%
      select(c("country", "Year", "fraction_name", "ISIC_Item", "SNA93 Item Code")) %>%
      filter(grepl("^C", fraction_name) | grepl("+C", 'SNA93 Item Code')) %>%
      mutate(manufacturing_flag = case_when(fraction_name == "C_AFSManuf" ~ "Estimated", TRUE ~ "UNIDO Observed")) %>%
        unique()
  
    # Merge manufacturing method flag back into the AFSValAdded_Rev4 data frame
        AFSValAdded_Rev4 <- left_join(AFSValAdded_Rev4, flag, by = c("country", "Year", "fraction_name", "ISIC_Item", "SNA93 Item Code"))

# Calculate AFS Value added
    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
      mutate(ValueAdded_LCU = ValueAdded * fraction_val) %>%
      select(-c(ValueAdded))

# Merge in GDP and population
    load(file = file.path(data_in, "BasicInfo_GDP.Rdata"))
    gdp_pop_info <- BasicInfo_GDP %>% 
      filter(GDP_breakdown == "Gross Domestic Product (GDP)") %>%
      rename(GDP = value,
             Year = year) %>%
      mutate(Year = as.numeric(Year)) %>%
      select(-c("GDP_breakdown"))
    
    # Join
        AFSValAdded_Rev4 <- left_join(AFSValAdded_Rev4, gdp_pop_info, by = c("ISO", "country", "m49_code", "Year"))

# Merge in exchange rates
    load(file = file.path(data_in, "ExchangeRates.Rdata"))
    ExRates <- ExchangeRates %>%
      mutate(Year = as.numeric(year)) %>%
      select(c(1,4,5,7,17))
    
    # Join 
    AFSValAdded_Rev4 <- left_join(AFSValAdded_Rev4, ExRates, by = c("country", "Year",  "ISO")) %>%
      rename(IMF_rate = "IMF based exchange rate",
             AMA_rate = "AMA exchange rate")

# Confirm year range
    range(AFSValAdded_Rev4$Year)
    
  isUnique(AFSValAdded_Rev4)
  duplicate_rows <- AFSValAdded_Rev4[duplicated(AFSValAdded_Rev4), ]
  
  AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>% unique()
  isUnique(AFSValAdded_Rev4)


```

$~$

Next, following the harmonization rules documented in the "ISIC3_ISIC4" data frame (from the "Classifications and metadata.xlsx" spreadsheet) we aggregate 1) food manufacturing with beverage manufacturing, and 2) electricity with water supply because these are grouped into single categories in ISIC Revision 3. 

```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# Rename the ISIC Items to combine the categories necessary to aggregate to harmonize across ISIC Revisions
    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
      # Rename the ISIC_Item to the harmonized name
          mutate(ISIC_Item = case_when(str_detect(ISIC_Item, pattern = "(?i)manufacture of food") ~ "Manufacture of food products and beverages",
                                       str_detect(ISIC_Item, pattern = "(?i)manufacture of beverages") ~ "Manufacture of food products and beverages",
                                       str_detect(ISIC_Item, pattern = "(?i)electricity") ~ "Electricity, gas, water",
                                       str_detect(ISIC_Item, pattern = "(?i)water supply") ~ "Electricity, gas, water",
                                            TRUE ~ ISIC_Item)) %>%
      # Rename the fraction so that we can combine the rows (the fraction value used is the same for both rows even though they were named separately)
          mutate(fraction_name = case_when(fraction_name == "D_Electric" ~ "DE_ElectricWater", 
                                           fraction_name == "E_Water" ~ "DE_ElectricWater", 
                                           TRUE ~ fraction_name)) %>%
      # Rename the SNA93 code
          mutate(`SNA93 Item Code` = case_when(fraction_name == "DE_ElectricWater" ~ "D+E",
                                               str_detect(ISIC_Item, pattern = "(?i)Manufacture of food products and beverages") ~ "C15", 
                                                          TRUE ~ `SNA93 Item Code`))
  # Now summarize ValueAdded_LCU by every other variable so that only the rows we want to sum together will be summed because the only value that differs on any variable between those two rows is the value added value (in other words: everything else is the same for the ones we want to combine except the value added)
    toaggregate <- AFSValAdded_Rev4 %>% 
        group_by(across(1:8)) %>%
        mutate(tosum = case_when(n() >1 ~ "sum", TRUE ~ "do nothing")) %>% 
        ungroup
    mostrows <- toaggregate %>%
      filter(tosum == "do nothing") %>%
      relocate(ValueAdded_LCU, .before = "Currency") %>%
      select(-c(tosum))
    addup <- toaggregate %>%
      filter(tosum == "sum") %>%
      group_by(across(-ValueAdded_LCU)) %>%
      summarise(ValueAdded_LCU = sum(ValueAdded_LCU, na.rm = TRUE), .groups = 'drop') %>%
      relocate(ValueAdded_LCU, .before = "Currency") %>%
      select(-tosum)    
    AFSValAdded_Rev4 <- rbind(mostrows, addup) 
  
  # Make sure the summation and recombination worked correctly - there should be no duplicates
    isUnique(AFSValAdded_Rev4)
    
  # Reorder the data
    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
      arrange("country", "year")

```

$~$

**Convert to current US dollars for comparison across countries.**

First, determine which exchange rate to apply. We check exchange rate discrepancies between the IMF and AMA rate to investigate when AMA rate should be used. See [@unitednationsstatisticsdivisionMethodologyNationalAccounts2008] for explanation of AMA rates and how they are used to adjust the exchange rate for economies undergoing rapid change where the IMF average period rate does not sufficiently account for this change (e.g., former Soviet states 1991-1994).
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# Test for discrepancies between IMF and AMA rate
    unit_test <- AFSValAdded_Rev4 %>%
      select(c("country", "ISO", "Currency", "Year", "AMA_rate", "IMF_rate")) %>%
      mutate(test = case_when(IMF_rate == AMA_rate ~ 1,
                              TRUE ~ 0)) %>%
    filter(test == 0 & !(is.na(AMA_rate))) 

# Check range of the unit test to confirm it operates correctly
    range(unit_test$test)

# Add a variable to indicate when the AMA rate should be used:
    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
      mutate(rate_to_use = case_when(IMF_rate == AMA_rate ~ "IMF",
                                      TRUE ~ "AMA"))
```

$~$

**Table 3. Country-years using alternative AMA exchange rate**
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Create table to show country-years where UN Stats has used an alternate exchange rate (AMA = Analysis of Main Aggregates, i.e., an exchange rate corrected for the purposes of accurate national accounts main aggregate statistics)
    AFSValAdded_Rev4 %>% select(c("country", "rate_to_use", "Year", "Currency")) %>%
      relocate("rate_to_use", .after = "Currency") %>%
      filter(rate_to_use != "IMF") %>%
      select(-c("rate_to_use")) %>%
      unique() %>% 
      group_by(country, Currency) %>%
      summarise(From = min(Year),
                To = max(Year)) %>%
    kable(col.names = c("Country/area", "Currency", "Years from", "to"), format = "html", caption = "Country-years using alternative AMA exchange rate") %>% kable_classic(full_width = T, html_font = "Cambria")
```

$~$

**Finally, we create indicators for analysis and visualization.**
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# Now create a variable that sums all the sectors
    AFSValAdded_sum_Rev4 <- AFSValAdded_Rev4 %>%
      group_by(country, m49_code, ISO, Year) %>%
      summarise(ValueAdded_AFS_LCU_Total = sum(ValueAdded_LCU, na.rm = TRUE))

# And merge back into the long data set (long by sectors/sub-sectors)
    AFSValAdded_Rev4 <- left_join(AFSValAdded_Rev4, AFSValAdded_sum_Rev4, by = c("country", "m49_code",  "ISO", "Year"))

# Now create sector and total value added as a share of GDP
    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>% 
      mutate(VA_per_GDP = (ValueAdded_LCU / GDP)*100)

    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
      mutate(VA_per_GDP_TOTAL = (ValueAdded_AFS_LCU_Total / GDP)*100) 

# Now convert to current US$ using the IMF exchange rate
    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
      mutate(ValueAdded_cUSD = case_when(rate_to_use == "IMF" ~ (ValueAdded_LCU / IMF_rate),
                                         rate_to_use == "AMA" ~ (ValueAdded_LCU / AMA_rate)),
             ValueAdded_AFS_cUSD_Total = case_when(rate_to_use == "IMF" ~ (ValueAdded_AFS_LCU_Total / IMF_rate),
                                         rate_to_use == "AMA" ~ (ValueAdded_AFS_LCU_Total / AMA_rate)),
             GDP_cUSD = case_when(rate_to_use == "IMF" ~ (GDP / IMF_rate),
                                  rate_to_use == "AMA" ~ (GDP / AMA_rate)))

# Now create per capita variables in cUSD
    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
      mutate(ValueAdded_cUSD_pc = (ValueAdded_cUSD / population),
             ValueAdded_AFS_cUSD_Total_pc = (ValueAdded_AFS_cUSD_Total / population))

# Reorganize the dataset
    groupA <- c("country", "ISO", "m49_code", "UN_continental_region")
    groupB <- c("Year", "ISIC_Item", "Is_AFS", "fraction_val")
    groupC <- c("GDP", "GDP_cUSD", "population", "IMF_rate", "AMA_rate", "rate_to_use")
    groupD <- c("ValueAdded_LCU", "ValueAdded_cUSD", "ValueAdded_cUSD_pc", "VA_per_GDP", 
                   "ValueAdded_AFS_LCU_Total", "ValueAdded_AFS_cUSD_Total", "ValueAdded_AFS_cUSD_Total_pc", "VA_per_GDP_TOTAL")

    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
      relocate(groupD, .before = "country")
    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
      relocate(groupC, .before = "ValueAdded_LCU")
    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
      relocate(groupB, .before = "GDP")
    AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
      relocate(groupA, .before = "Year")

isUnique(AFSValAdded_Rev4)

    # Now filter value added = NA so that the correct ISIC Revision by country-year will be selected
      # For example, China is in the UNIDO Rev 4 dataset for 2008-2017 but actually has only the 
      # Main aggregate as non-missing
      AFSValAdded_Rev4 <- AFSValAdded_Rev4 %>%
        filter(!(is.na(ValueAdded_LCU)))

```

$~$

#### ISIC Revision 3

Next, we repeat the merging of SNA and UNIDO data for ISIC Revision 3
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# First select the main aggregates data
    load(file = file.path(data_in, "AgriFood_sum_Rev3.RData"))
    isUnique(AgriFood_sum_Rev3)
    
    MainAggregates_Rev3 <- AgriFood_sum_Rev3 %>%
      filter(SNA_Item != "Equals: GROSS DOMESTIC PRODUCT") %>% # filter out GDP as a row
      # Now rename the ISIC_Item column usng the harmonized category name (see the ISIC3_ISIC4 crosswalk)
      mutate(ISIC_Item = case_when(is.na(ISIC_Item) & str_detect(SNA_Item, pattern = "(?i)Agriculture") ~ "Agriculture, forestry and fishing",
                                   is.na(ISIC_Item) & str_detect(SNA_Item, pattern = "(?i)Land transport") ~ "Transportation and storage",
                                   TRUE ~ ISIC_Item)) %>%
      select(c("country", "ISO", "m49_code", "Year", "ISIC_Item", "ValueAdded", "Is_AFS", "SNA93 Item Code")) %>%
      filter(!(Is_AFS = 0)) %>%
      # Make sure the country names are correct
          mutate(country = case_when(country == "Venezuela, Bolivarian Republic of" ~ "Venezuela (Bolivarian Republic of)",
                               country == "Côte D'Ivoire" ~ "Côte d'Ivoire",
                               TRUE ~ country))
  isUnique(MainAggregates_Rev3)

# Next select the manufacturing data
    load(file = file.path(data_in, "ManufVA_Rev3.RData"))
    isUnique(ManufVA_Rev3)
      
    Manufacturing_Rev3 <- ManufVA_Rev3 %>%
      filter(Is_AFS != 0) %>% # filter out the non-AFS categories
      select(c("country", "ISO", "m49_code", "Year", "ISIC_Item", "value", "Is_AFS")) %>%
      unique() %>%
      rename(ValueAdded = value) %>%
      filter(ISIC_Item != "Manufacturing") %>% ## Remove aggregate
      # Drop Recycling as there is no fraction to estimate the disaggregation - note this limitation
      filter(ISIC_Item != "Recycling") %>%
      mutate(Year = as.character(Year)) %>%
      mutate(Year = as.numeric(Year)) 
    
  isUnique(Manufacturing_Rev3)
  dups <- Manufacturing_Rev3[duplicated(Manufacturing_Rev3),]
  
```

$~$

**Table 4. Countries with no ISIC Rev 3 manufacturing sector disaggregated data in UNIDO database**
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Identify countries with no manufacturing data in the UNIDO database
    no_UNIDO_data_Rev3 <- anti_join(MainAggregates_Rev3[, c("country", "Year")], Manufacturing_Rev3[, c("country", "Year")],
                               by = c("country", "Year")) %>% unique()

# Create table
    kable(no_UNIDO_data_Rev3, "html", caption = "Countries with no ISIC Rev 3 manufacturing sector disaggregated data in UNIDO database") %>% 
      kable_classic(full_width = F, html_font = "Cambria")
```

$~$

Now remove manufacturing only for countries that HAVE the UNIDO data.
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# Now remove manufacturing only for countries that HAVE the UNIDO data
# We use the country list from the anti-join step above to identify these countries.
    no_UNIDO_data_Rev3$hasUNIDO <- 0
    MainAggregates_Rev3 <- left_join(MainAggregates_Rev3, no_UNIDO_data_Rev3, by = c("country", "Year")) %>%
      mutate(hasUNIDO = case_when(is.na(hasUNIDO) ~ 1,
                                   TRUE ~ hasUNIDO))
      
    MainAggregates_Rev3 <- MainAggregates_Rev3 %>%
      filter(!(hasUNIDO == 1 & ISIC_Item == "Manufacturing")) 
    
# Now add the SNA93 Item Code variable to the manufacturing data set
    Manufacturing_Rev3$"SNA93 Item Code" <- "D"
    
# Finally, we have to make sure we're not including manufacturing data for country-years that do not have main aggregates, so we repeat the anti-join. 
    no_SNA_data_Rev3 <- anti_join(Manufacturing_Rev3[, c("country", "Year")], MainAggregates_Rev3[, c("country", "Year")], by = c("country", "Year")) %>% unique()

# Create table
    kable(no_SNA_data_Rev3, "html", caption = "Countries with no ISIC Rev 3 SNA data but do have UNIDO manufacturing data") %>% 
      kable_classic(full_width = F, html_font = "Cambria")
    
    # Remove from manufacturing data frame
    no_SNA_data_Rev3$hasSNA <- 0 
    Manufacturing_Rev3 <- left_join(Manufacturing_Rev3, no_SNA_data_Rev3, 
                                     by = c("country", "Year")) %>%
      mutate(hasSNA = case_when(is.na(hasSNA) ~ 1,
                                   TRUE ~ hasSNA)) %>%
      filter(hasSNA == 1) 


# Now append the manufacturing data to the main aggregates data for the country-years with UNIDO data at the ISIC Rev 3 level
    MainAggregates_Rev3 <- MainAggregates_Rev3 %>% select(-c("hasUNIDO"))
    Manufacturing_Rev3 <- Manufacturing_Rev3 %>% select(-c("hasSNA"))
    AFSValAdded_Rev3 <- rbind(MainAggregates_Rev3, Manufacturing_Rev3) %>%
      arrange(country, Year)
    isUnique(AFSValAdded_Rev3)
```

$~$

**Table 5. ISIC Categories in Agrifood System at level where data are available - ISIC Rev 3**
Note, this table repeats from Script #2
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Rename the ISIC_Item values to match the fractions
    AFSValAdded_Rev3 %>% select(c("ISIC_Item")) %>%
      unique() %>% mutate(ISIC_Item = as.factor(ISIC_Item)) %>% 
      arrange(ISIC_Item) %>%
      kable("html", caption = "ISIC Categories in Agrifood System at level where data are available") %>% 
      kable_classic(full_width = F, html_font = "Cambria")
```

**Merge in the fractions and calculate AFS shares.**
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# Rename the ISIC Items required for the join
    isUnique(AFSValAdded_Rev3)
    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>% 
      mutate(fraction_name = case_when(str_detect(ISIC_Item, pattern = "(?i)mining") ~ "C_Mining",
                                   ISIC_Item == "Manufacturing" ~ "D_AFSManuf",
                                   str_detect(ISIC_Item, pattern = "(?i)textile") ~ "D17_Textiles",
                                   str_detect(ISIC_Item, pattern = "(?i)wearing apparel") ~ "D18_WearingApparel",
                                   str_detect(ISIC_Item, pattern = "(?i)leather") ~ "D19_Leather",
                                   str_detect(ISIC_Item, pattern = "(?i)chemicals") ~ "D24_Chemicals", 
                                   str_detect(ISIC_Item, pattern = "(?i)rubber") ~ "D25_Rubber", 
                                   str_detect(ISIC_Item, pattern = "(?i)machinery") ~ "D29_Machinery", 
                                   str_detect(ISIC_Item, pattern = "(?i)furniture") ~ "D36_Furniture",
                                   str_detect(ISIC_Item, pattern = "(?i)wholesale") ~ "G_Trade",
                                   str_detect(ISIC_Item, pattern = "(?i)Electricity") ~ "E_Electric",
                                   str_detect(ISIC_Item, pattern = "(?i)retail") ~ "G_Trade",
                                   str_detect(ISIC_Item, pattern = "(?i)hotels") ~ "H_HotelsRestaurants",
                                   str_detect(ISIC_Item, pattern = "(?i)transport") ~ "I_Transport",
                                   str_detect(ISIC_Item, pattern = "(?i)renting") ~ "K_Rentals",
                                   str_detect(ISIC_Item, pattern = "(?i)public administration") ~ "L_PubAdmin",
                                   str_detect(ISIC_Item, pattern = "(?i)health") ~ "N_HealthSocWork",
                               Is_AFS == 1 ~ "1")) # Replace fraction = 1 for categories that are wholly AFS (Is_AFS = 1)
    isUnique(AFSValAdded_Rev3)

# Now add the fractions
    load(file = file.path(data_in, "fractions_Rev3.Rdata"))
    
      # Quick fix removing duplicates - need to go back to where they are created to fix
        # Diagnose:
          # fractions_Rev3 <- fractions_Rev3 %>%
          #   distinct(ISO, Year, fraction_name, .keep_all = TRUE)
          # duplicates <- fractions_Rev3 %>%
          #   group_by(across(everything())) %>%  # Group by all columns
          #   filter(n() > 1) %>%                  # Keep only groups with duplicates
          #   ungroup()
      fractions_Rev3 <- fractions_Rev3 %>% unique()
      isUnique(fractions_Rev3)

    AFSValAdded_Rev3 <- left_join(AFSValAdded_Rev3, fractions_Rev3, by = c("ISO", "Year", "fraction_name"))
    isUnique(AFSValAdded_Rev3)

# Replace fraction = 1 for wholly AFS 
    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>%
      mutate(fraction_val = case_when(Is_AFS == 1 ~ 1,
                                         TRUE ~ fraction_val))
    isUnique(AFSValAdded_Rev3)
    
# Add in the second fraction for disaggregating manufacturing
    D_AFSInputManuf <- fractions_Rev3 %>% filter(fraction_name == "D_AFSInputManuf") %>%
      rename(D_AFSInputManuf = fraction_val) %>% select(-c(fraction_name))
    AFSValAdded_Rev3 <- left_join(AFSValAdded_Rev3, D_AFSInputManuf, by = c('ISO', 'Year')) 
    isUnique(AFSValAdded_Rev3)

# Sum the AFS Manufacturing fractions so that the share of manufacturing attributed to AFS is the share of manufacturing of AFS production AND the share of manufacturing that is inputs into AFS production
    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>%
      mutate(fraction_val = case_when(ISIC_Item == "Manufacturing" ~ (fraction_val + D_AFSInputManuf), TRUE ~ fraction_val)) %>%
      select(-c("D_AFSInputManuf"))
    isUnique(AFSValAdded_Rev3)

# Create a flag variable to indicate which country-years have only 2 disaggregations for manufacturing (AFS-based products, AFS production inputs), which are in other words the country-years where we use the fraction method to disaggregate. This flag is important because no country-years will have data for the estimated disaggregations if it had data in the UNIDO data base and vice versa, so we will need to accommodate for this in the visualizations if combining across the estimated and observed manufacturing disaggregates. 
    flag <- AFSValAdded_Rev3 %>%
      select(c("country", "Year", "fraction_name", "ISIC_Item", "SNA93 Item Code")) %>%
      filter(grepl("^D", fraction_name) | grepl("+D", 'SNA93 Item Code')) %>%
      mutate(manufacturing_flag = case_when(fraction_name == "D_AFSManuf" ~ "Estimated",
                                            TRUE ~ "UNIDO Observed")) %>%
        unique()
  
    # Merge manufacturing method flag back into the AFSValAdded_Rev3 data frame
        AFSValAdded_Rev3 <- left_join(AFSValAdded_Rev3, flag, by = c("country", "Year", "fraction_name",    "ISIC_Item", "SNA93 Item Code"))

# Calculate AFS Value added
    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>%
      mutate(ValueAdded_LCU = ValueAdded * fraction_val) %>%
      select(-c(ValueAdded))
    isUnique(AFSValAdded_Rev3)

# Merge in GDP and population
    AFSValAdded_Rev3 <- left_join(AFSValAdded_Rev3, gdp_pop_info, by = c("ISO", "country", "m49_code", "Year")) 
    # This creates duplicates of Sudan, remove before proceeding with unique()
      AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>% unique()
    isUnique(AFSValAdded_Rev3)

# Merge in exchange rates
    AFSValAdded_Rev3 <- left_join(AFSValAdded_Rev3, ExRates, by = c("country", "Year", "ISO")) %>%
      rename(IMF_rate = "IMF based exchange rate",
             AMA_rate = "AMA exchange rate") %>%
      unique()

# Drop years outside of 1995-2021, that is the only period in the EORA data
    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>% filter(Year >= 1995) %>% 
      filter(Year <= 2021) 
   isUnique(AFSValAdded_Rev3)   
   
```

$~$

**Convert to current US dollars for comparison across countries.**
First, determine which exchange rate to apply. We check exchange rate discrepancies between the IMF and AMA rate to investigate when AMA rate should be used. See [@unitednationsstatisticsdivisionMethodologyNationalAccounts2008] for explanation of AMA rates and how they are used to adjust the exchange rate for economies undergoing rapid change where the IMF average period rate does not sufficiently account for this change (e.g., former Soviet states 1991-1994).
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# Test for discrepancies between IMF and AMA rate
    unit_test <- AFSValAdded_Rev3 %>%
      select(c("country", "ISO", "Currency", "Year", "AMA_rate", "IMF_rate")) %>%
      mutate(test = case_when(IMF_rate == AMA_rate ~ 1,
                              TRUE ~ 0)) %>%
    filter(test == 0 & !(is.na(AMA_rate))) 
    range(unit_test$test) 

# Add a variable to indicate when the AMA rate should be used:
    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>%
      mutate(rate_to_use = case_when(IMF_rate == AMA_rate ~ "IMF",
                                      TRUE ~ "AMA"))
```

$~$

**Table 6. Country-years using alternative AMA exchange rate, ISIC Rev 3**
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Create table to rate to use
    AFSValAdded_Rev3 %>% select(c("country", "rate_to_use", "Year", "Currency")) %>%
      relocate("rate_to_use", .after = "Currency") %>%
      filter(rate_to_use != "IMF") %>% 
      select(-c("rate_to_use")) %>%
      unique() %>% 
      group_by(country, Currency) %>%
      summarise(From = min(Year),
                To = max(Year)) %>%
    kable(col.names = c("Country/area", "Currency", "Years from", "to"), format = "html", caption = "Country-years using alternative AMA exchange rate") %>% kable_classic(full_width = T, html_font = "Cambria")
```

$~$

**Finally, we create indicators for analysis and visualization.**
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# Now create a variable that sums all the sectors
    AFSValAdded_sum_Rev3 <- AFSValAdded_Rev3 %>%
      group_by(country, m49_code, ISO, Year) %>%
      summarise(ValueAdded_AFS_LCU_Total = sum(ValueAdded_LCU, na.rm = TRUE))
    isUnique(AFSValAdded_sum_Rev3)

# And merge back into the long dataset
    AFSValAdded_Rev3 <- left_join(AFSValAdded_Rev3, AFSValAdded_sum_Rev3, by = c("country", "m49_code", "ISO", "Year"))
    isUnique(AFSValAdded_Rev3)

# Now create sector and total value added as a share of GDP
    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>% 
      mutate(VA_per_GDP = (ValueAdded_LCU / GDP)*100)
    
    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>%
      mutate(VA_per_GDP_TOTAL = (ValueAdded_AFS_LCU_Total / GDP)*100) 

# Now convert to current US$ using the IMF exchange rate
    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>%
      mutate(ValueAdded_cUSD = case_when(rate_to_use == "IMF" ~ (ValueAdded_LCU / IMF_rate),
                                         rate_to_use == "AMA" ~ (ValueAdded_LCU / AMA_rate)),
             ValueAdded_AFS_cUSD_Total = case_when(rate_to_use == "IMF" ~ (ValueAdded_AFS_LCU_Total / IMF_rate),
                                         rate_to_use == "AMA" ~ (ValueAdded_AFS_LCU_Total / AMA_rate)),
             GDP_cUSD = case_when(rate_to_use == "IMF" ~ (GDP / IMF_rate),
                                  rate_to_use == "AMA" ~ (GDP / AMA_rate)))

# Now create per capita variables in cUSD
    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>%
      mutate(ValueAdded_cUSD_pc = (ValueAdded_cUSD / population),
             ValueAdded_AFS_cUSD_Total_pc = (ValueAdded_AFS_cUSD_Total / population))

# Reorganize the dataset
    groupA <- c("country", "ISO", "m49_code", "UN_continental_region")
    groupB <- c("Year", "ISIC_Item", "Is_AFS", "fraction_val")
    groupC <- c("GDP", "GDP_cUSD", "population", "IMF_rate", "AMA_rate", "rate_to_use")
    groupD <- c("ValueAdded_LCU", "ValueAdded_cUSD", "ValueAdded_cUSD_pc", "VA_per_GDP", 
                   "ValueAdded_AFS_LCU_Total", "ValueAdded_AFS_cUSD_Total", "ValueAdded_AFS_cUSD_Total_pc", "VA_per_GDP_TOTAL")

    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>%
      relocate(groupD, .before = "country")
    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>%
      relocate(groupC, .before = "ValueAdded_LCU")
    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>%
      relocate(groupB, .before = "GDP")
    AFSValAdded_Rev3 <- AFSValAdded_Rev3 %>%
      relocate(groupA, .before = "Year")

    isUnique(AFSValAdded_Rev3)
    
```

$~$

#### Create the combined time series based on both ISIC Revision 3 and ISIC Revision 4 data
In order to get to a final time series with one set of observations per country-year (either ISIC Rev 3 OR ISIC Rev 4 for any given country-year) we need to identify the overlapping observations (which are country-years with data for both ISIC Rev 3 and ISIC Rev 4). Where there are both ISIC Revisions, we want to keep only ISIC Rev 4 in our final dataset, unless ISIC Rev 3 has UNIDO data and ISIC Rev 4 does not have UNIDO data. This leads to a multi-step merge process:

-   Step 1: Identify country-years with ISIC Rev 3 that do not have ISIC Rev 4 data
-   Step 2: Identify country-years without ISIC Rev 4 data but that do have ISIC Rev 3 UNIDO data
-   Step 3: Build the final dataset as:
    -   ISIC Rev 3 where there are no ISIC Rev 4 data or no ISIC Rev 4 UNIDO data
    -   ISIC Rev 4 where there are Rev 4 main aggregates and UNIDO data
    -   ISIC Rev 4 where there is no Rev 3 main aggregates even though there are no UNIDO data
    
Note: China in 2020 has only Revision 4 main aggregate data and only Revision 3 manufacturing data. Following the data selection process below would result in only Revision 3 manufacturing data in the final dataset. We manually ensure that Revision 4 main aggregate data for China in 2020 are included and use the manufacturing estimate instead, following the principle of not mixing ISIC Revisions within country-year across the two data sources.    
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# First we add an identifying variable to each data frame to indicate the ISIC Revision that was used for that record
    AFSValAdded_Rev3$ISIC_Revision <- 3
    AFSValAdded_Rev4$ISIC_Revision <- 4
    
# We use anti_join to identify the ISIC Revision 3 data that are not duplicate country-years with ISIC Revision 4
    # This drops any records from the AFSValAdded_Rev3 data frame that are for country-years also present in the AFSValAdded_Rev4 data frame.
    AFSValAdded_Rev3_unique <- anti_join(AFSValAdded_Rev3, AFSValAdded_Rev4, 
                                         by = c("country", "Year")) 
    
# Now we identify country-years where there is Rev 4 data for the main aggregates but no UNIDO data
    AFSValAdded_Rev4_noUNIDO <- AFSValAdded_Rev4 %>% 
      filter(is.na(manufacturing_flag) | manufacturing_flag == "Estimated")
    AFSValAdded_Rev3_wUNIDO <- AFSValAdded_Rev3 %>%
      filter(manufacturing_flag == "UNIDO Observed")
    # Now use an inner join to keep only the country-years that are estimated in Rev 4 but have UNIDO data in Rev 3
    AFSValAdded_useRev3forthese <- inner_join(AFSValAdded_Rev3_wUNIDO,
                                              AFSValAdded_Rev4_noUNIDO, 
                                              by = c("country", "Year")) %>%
      select(c("country","Year")) %>% unique()
    AFSValAdded_useRev3forthese$Rev3 <- 1

# Now remove from the Rev 4 data the country-years where Rev 3 is preferred
    AFSValAdded_Rev4_selected <- left_join(AFSValAdded_Rev4, AFSValAdded_useRev3forthese, by = c("country", "Year")) %>%
      filter(is.na(Rev3)) %>% select(-c(Rev3))

# Now re-run the anti-join to keep only the Rev 3 observations that are country-years not in the final selection of country-years using Rev 4
    AFSValAdded_Rev3_unique <- anti_join(AFSValAdded_Rev3, AFSValAdded_Rev4_selected, by = c("country", "Year")) 
```

$~$

**Carry out remaining harmonization actions.**
Finally, we carry out the remaining harmonization actions and then append the ISIC Revision 3 data set to ISIC Rev 4.
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# We use the AFSValAdded_Rev3_unique data frame for Revision 3 so that we do not introduce any country-year records included in the Rev 4 data set

# Harmonize ISIC Item names
    AFSValAdded_Rev3_unique <- AFSValAdded_Rev3_unique %>%
      mutate(ISIC_Item = case_when(str_detect(ISIC_Item, pattern = "(?i)wearing apparel") ~ "Manufacture of wearing apparel",
                                   str_detect(ISIC_Item, pattern = "(?i)leather") ~ "Manufacture of leather and related products",
                                   str_detect(ISIC_Item, pattern = "(?i)manufacture of wood") ~ "Manufacture of wood and wood products",
                                   str_detect(ISIC_Item, pattern = "(?i)manufacture of furniture") ~ "Manufacture of furniture",
                                   str_detect(ISIC_Item, pattern = "(?i)transport") ~ "Transportation and storage",
                                   str_detect(ISIC_Item, pattern = "(?i)electricity") ~ "Electricity, gas, water",
                                   str_detect(ISIC_Item, pattern = "(?i)wholesale and retail trade") ~ "Wholesale and retail trade",
                                   str_detect(ISIC_Item, pattern = "(?i)hotels") ~ "Food service",
                                   str_detect(ISIC_Item, pattern = "(?i)real estate") ~ "Professional, scientific and technical activities",
                                   ISIC_Item == "Professional, scientific, technical, administrative and support service activities" ~ "Professional, scientific and technical activities",
                                   str_detect(ISIC_Item, pattern = "(?i)public administration") ~ "Public administration",
                                   TRUE ~ ISIC_Item))

    AFSValAdded_Rev4_selected <- AFSValAdded_Rev4_selected %>%
      mutate(ISIC_Item = case_when(str_detect(ISIC_Item, pattern = "(?i)manufacture of wood") ~ "Manufacture of wood and wood products",
                                   str_detect(ISIC_Item, pattern = "(?i)manufacture of basic pharmaceutical") ~ "Manufacture of pharmaceuticals",
                                   str_detect(ISIC_Item, pattern = "(?i)wholesale and retail trade") ~ "Wholesale and retail trade",
                                   str_detect(ISIC_Item, pattern = "(?i)accommodation and food") ~ "Food service",
                                   str_detect(ISIC_Item, pattern = "(?i)real estate") ~ "Professional, scientific and technical activities",
                                   str_detect(ISIC_Item, pattern = "(?i)public administration") ~ "Public administration",
                                   ISIC_Item == "Professional, scientific, technical, administrative and support service activities" ~ "Professional, scientific and technical activities",
                                TRUE ~ ISIC_Item))

    AFS_ValueAdded <- rbind(AFSValAdded_Rev4_selected, AFSValAdded_Rev3_unique) %>%
      arrange(country, Year)
    
    isUnique(AFS_ValueAdded)

# Now drop areas that are not UN Member states
  # Confirm all UN Member state information is correctly matched
      AFS_ValueAdded %>% select(c("country", "UNmemberstate")) %>% unique() %>%
        filter(is.na(UNmemberstate)) %>%
        kable(col.names = c("Country/area", "member state"), format = "html", caption = "Check for UN Member state identification") %>%
        kable_classic(full_width = T, html_font = "Cambria")
    
    AFS_ValueAdded <- AFS_ValueAdded %>% filter(UNmemberstate == "Yes")
      AFS_ValueAdded %>% select(c("country", "UNmemberstate")) %>% unique() %>%
        kable(col.names = c("Country/area", "member state"), format = "html", caption = "Check for UN Member state identification") %>%
        kable_classic(full_width = T, html_font = "Cambria")

# Remove the unused factor levels in the ISIC_Item variable
    AFS_ValueAdded <- AFS_ValueAdded %>%
      mutate(ISIC_Item = as.factor(ISIC_Item)) %>%
      droplevels("ISIC_Item")
    levels(AFS_ValueAdded$ISIC_Item)
```

$~$

Now we confirm there are no duplicates. Note that there are some countries that have gaps in ISIC Revision 4 where ISIC Rev 3 is used, in other words the individual country series switches from Rev 4 to 3 and back again. This can be observed in the duplicates data set, for example see Albania 2016 and 2021 use Rev 3, whereas the years before and between them use Revision 4. 
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
isUnique(AFS_ValueAdded)

```

$~$

**Country-year ISIC Revision**
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Set up the data
    tabledata <- AFS_ValueAdded %>% 
      select(c(country, Year, ISIC_Revision)) %>%
      rename(Country = country) %>%
      unique() 

# Print it as a heatmap
    ggplot(tabledata, 
           aes(y = factor(Country, levels = rev(levels(factor(Country)))), 
               x = factor(Year), fill = factor(ISIC_Revision))) +
      geom_tile() +
      scale_fill_brewer(palette = "Paired", na.value = "white") +
      theme_classic() +
      theme(axis.text.x = element_text(size = 6, angle = 90, vjust = 0.5),
            axis.text.y = element_text(size = 4),
            legend.position = "bottom") +
      labs(x = "", y = "", fill = "ISIC Revision") 
```

$~$

**Table 7. ISIC Item Codes and Remaining Combined categories by country and ISIC Revision**
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Document the ISIC Items, and note the remaining combined categories
    AFS_ValueAdded %>% select(c("country", "Year", "ISIC_Item", "SNA93 Item Code", "ISIC_Revision")) %>%
      unique() %>% 
      relocate(Year, .after = "ISIC_Revision") %>%
      group_by(country, ISIC_Item, `SNA93 Item Code`, ISIC_Revision) %>%
      summarise(From = min(Year),
                To = max(Year)) %>%
    kable(col.names = c("Country", "ISIC Item", "SNA93 Item Code", "ISIC_Revision", "Years from", "to"), format = "html", caption = "ISIC Item Codes and Remaining Combined categories by country and ISIC Revision") %>% kable_classic(full_width = T, html_font = "Cambria")
```

$~$

**Table 8. Number of observations (countries) per year**
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Countries per year
    AFS_ValueAdded %>% select(c("country", "Year")) %>%
      unique() %>% relocate(Year, .before = country) %>%
      group_by(Year) %>%
      summarise(n = n()) %>%
    kable(col.names = c("Year", "Number of Countries"), format = "html", caption = "Number of countries per year in the data set") %>%
    kable_classic(full_width = T, html_font = "Cambria")
```

$~$

**Data quality checks**
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# Remove the "Other community, social and personal service activities" ISIC category which was not dropped successfully earlier
    AFS_ValueAdded <- AFS_ValueAdded %>% filter(ISIC_Item != "Other community, social and personal service activities")
    isUnique(AFS_ValueAdded)

# Identify any cases where the AFS value added as a share of GDP is >100
improbable_cases <- AFS_ValueAdded %>% filter(VA_per_GDP_TOTAL >100) %>% 
  select(c(country, Year, ValueAdded_AFS_cUSD_Total_pc, VA_per_GDP_TOTAL, rate_to_use)) %>% unique() %>%
  filter(!(is.na(ValueAdded_AFS_cUSD_Total_pc)))

# Identify any cases with negative value added
negative_valadded <- AFS_ValueAdded %>% filter(ValueAdded_LCU < 0 & !(is.na(ValueAdded_LCU))) 

# Create table
    kable(improbable_cases, format = "html", caption = "Improbable cases") %>%
      kable_classic(full_width = T, html_font = "Cambria")
    
# Replace improbable cases as NA
    # First document the improbable total AFS value added as a share of GDP in an improbable case variable  
    AFS_ValueAdded <- AFS_ValueAdded %>%
      mutate(improbable_VAperGDPtotal = case_when((country == "Belarus" & Year %in% 1995:2013) | 
                                                    (country == "Ukraine" & Year == 1995) |
                                                    (country == "Kyrgyzstan" & Year == 1995) |
                                                    (country == "Uzbekistan" & Year == 1995) |
                                                    (country == "Sao Tome and Principe" & Year %in% 2001:2020) |
                                                    (country == "Ghana" & Year %in% 1995:1999) |
                                                    (country == "Turkmenistan" & Year %in% 1995:2003) |
                                                    (country == "Venezuela (Bolivarian Republic of)" & Year %in% 2005:2019) ~ VA_per_GDP_TOTAL, 
               TRUE ~ NA))
    
    # Now mutate across the columns of value added and related indicators to replace improbably country-years with NA
        AFS_ValueAdded <- AFS_ValueAdded %>%
            mutate(across(15:22, ~ ifelse(country == "Belarus" & Year %in% 1995:2013, NA, .)),
                   across(15:22, ~ ifelse(country == "Sao Tome and Principe" & Year %in% 2001:2020, 
                                          NA, .)),
                   across(15:22, ~ ifelse(country == "Ukraine" & Year==1995, 
                                          NA, .)),
                   across(15:22, ~ ifelse(country == "Kyrgyzstan" & Year==1995, 
                                          NA, .)),
                   across(15:22, ~ ifelse(country == "Uzbekistan" & Year==1995, 
                                          NA, .)),
                   across(15:22, ~ ifelse(country == "Ghana" & Year %in% 1995:1999, 
                                          NA, .)),
                   across(15:22, ~ ifelse(country == "Turkmenistan" & Year %in% 1995:2003, NA, .)),
                   across(15:22, ~ ifelse(country == "Venezuela (Bolivarian Republic of)" & Year %in% 2005:2019, NA, .)))
    isUnique(AFS_ValueAdded)

# Now add in the quality flag related to multiple series
    multseries_flag <- multseries_flag %>% unique()
    AFS_ValueAdded <- left_join(AFS_ValueAdded, multseries_flag, by = "country")
   isUnique(AFS_ValueAdded)
 
# Finally factor variables
    cols <- c(1:2,14,23:26,35,37)
    AFS_ValueAdded <- AFS_ValueAdded %>% 
      mutate(across(cols, as.factor))
        
check <- AFS_ValueAdded %>%
  select(c(country, Year)) %>% unique()
summary(check)
unique(check$country)

# Ensure unique 
  isUnique(AFS_ValueAdded)

# Save the final data set
    save(AFS_ValueAdded, file = file.path(data_out, "AFS_ValueAdded.RData"))
    
    # Write to .xlsx to port to other software
      writexl::write_xlsx(AFS_ValueAdded, path = file.path(data_out, "AFS_ValueAdded.xlsx"))
    
# Clean up
rm(check, improbable_cases, multseries_flag)
    
```
Note: the following observations have been replaced as missing due to improbable value added (total value added from AFS multiple times GDP):

-   Belarus: 1995-2013
-   Ghana: 1995-1999
-   Sao Tome and Principe: 2001-2020
-   Turkmenistan: 1995-2003
-   Venezuela: 2005-2019 -- FAOSTAT also does not report value added from agriculture as a share of GDP for Venezuela.
-   Syria: 2000 has negative 

$~$

**References**
