---
title: "Schneider_ESS Working Paper_Analysis Replication"
author: "Kate Schneider Lecy"
date: "`r Sys.Date()`"
output: html_document
---

### *Summary of Script*
This script contains the replication code to create the tables and figures presented in the ESS working paper by Schneider et al. entitled "Estimating output value added in the world's agrifood systems" 

```{r setup, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
### Setup required to knit this script into a markdown document

    # Load the knitr package
      library(knitr)
    
    # Set echo = FALSE for all code chunks will prevent the code from printing in the output file
      knitr::opts_chunk$set(echo = FALSE)
      
# Set the root folder to the project root so that all file paths are relative to the main project folder
    knitr::opts_knit$set('./')
  
# Set the treatment of numbers to numerical (avoids scientific notation from showing in results)
    options(scipen = 999)

# Load packages
    # R studio should prompt the installation of any packages not loaded on the instance where this script has been opened
    
    # Data management packages
    library(tidyverse)
    library(here)
    library(labelled)
    library(kableExtra)
    library(purrr)
    library(citr) ## To install from github: devtools::install_github("crsh/citr")
    library(scales)
    library(broom)
    library(ggpubr)
    
    # Visualization and table packages
    library(pals)
    library(cowplot)
    library(flextable)
    library(ggplot2)

# Set relative directory paths
    data_in <- here::here("Input Data")
    fig_out <- here::here("Figures")
    support <- here::here("Support files and scripts")
    data_out <- here::here("Output Datasets")

# Create a "not in" operator
    `%notin%` <- Negate(`%in%`) 

# Note: "$~$" adds line breaks in the html report in the knitting process.

# Color palette with 26 discrete differentiated values
  unname(alphabet())
  unname(pals::brewer.blues(13))
  
  # Set the colors to the specific ISIC category name so they are consistent across figures
  # Even when only a subset of the ISIC codes are present
  colors <- c("Agriculture, forestry and fishing" ="#005C31",
              "Electricity, gas, water" = "#4C005C",
              "Food service" = "#808080",
              "Health and social work" = "#FFA8BB",
              "Manufacture of chemicals and chemical products" = "#21618C",                
              "Manufacture of food products and beverages" = "#2874A6",
              "Manufacture of furniture" = "#A9CCE3",
              "Manufacture of leather and related products" = "#1A5276",
              "Manufacture of machinery and equipment n.e.c." = "#1B4F72",              
              "Manufacture of paper and paper products" = "#D6EAF8",
              "Manufacture of pharmaceuticals" = "#21618C",
              "Manufacture of rubber and plastics products" = "#154360",
              "Manufacture of textiles" = "#5499C7",
              "Manufacture of tobacco products" = "#3498DB",
              "Manufacture of wearing apparel" = "#2471A3",
              "Manufacture of wood and wood products" = "#85C1E9",
              "Manufacturing (where only aggregate data available)" = "#1B4F72",
              "Manufacturing, mining and quarrying and other industrial activity (Manufacturing share if disaggregate data are not available)" = "#1B4F72",
              "Mining and quarrying" = "#5EF1F2",
              "Professional, scientific and technical activities" = "#FFFF80",
              "Public administration" = "#F0A0FF",
              "Transportation and storage" = "#C20088",
              "Wholesale and retail trade" = "#00998F")

```

$~$

# Data management

```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
# Load the data set
    load(file = file.path(data_out, "AFS_ValueAdded.RData"))

# Shorten country names for visualization 
    AFS_ValueAdded <- AFS_ValueAdded %>%
      mutate(country = case_when(country == "United Kingdom of Great Britain and Northern Ireland" ~ "United Kingdom",
                                 country == "Bolivia (Plurinational State of)" ~ "Bolivia",
                                 country == "Gambia (Republic of The)" ~ "The Gambia",
                                 country == "Iran (Islamic Republic of)" ~ "Iran",
                                 country == "United States of America" ~ "United States",
                                 country == "United Republic of Tanzania" ~ "Tanzania",
                                 country == "Lao People’s Democratic Republic" ~ "Lao PDR",
                                 TRUE ~ country))

# Revise ISIC categories for explanation
    AFS_ValueAdded <- AFS_ValueAdded %>%
      mutate(ISIC_Item = case_when(ISIC_Item == "Manufacturing" ~ "Manufacturing (where only aggregate data available)",
                                   ISIC_Item == "Manufacturing, mining and quarrying and other industrial activities" ~ "Manufacturing, mining and quarrying and other industrial activity (Manufacturing share if disaggregate data are not available)",
                                   TRUE ~ ISIC_Item))
    
# Reorder the ISIC Items
    AFS_ValueAdded <- AFS_ValueAdded %>%
      mutate(ISIC_order = case_when(ISIC_Item == "Agriculture, forestry and fishing" ~ 1,
                                    ISIC_Item == "Manufacturing (where only aggregate data available)" ~ 2,
                                    ISIC_Item == "Manufacture of food products and beverages" ~ 3,
                                    ISIC_Item == "Manufacture of tobacco products" ~ 4,
                                    ISIC_Item == "Manufacture of wood and wood products" ~ 5,
                                    ISIC_Item == "Manufacture of paper and paper products" ~ 6,
                                    ISIC_Item == "Manufacture of furniture" ~ 7,
                                    ISIC_Item == "Manufacture of textiles" ~ 8,
                                    ISIC_Item == "Manufacture of wearing apparel" ~ 9,
                                    ISIC_Item == "Manufacture of leather and related products" ~ 10,
                                    ISIC_Item == "Manufacture of rubber and plastics products" ~ 11,
                                    ISIC_Item == "Manufacture of chemicals and chemical products" ~ 12,
                                    ISIC_Item == "Manufacture of pharmaceuticals" ~ 13,
                                    ISIC_Item == "Manufacture of machinery and equipment n.e.c." ~ 14,
                                    ISIC_Item == "Manufacturing, mining and quarrying and other industrial activity (Manufacturing share if disaggregate data are not available)" ~ 15,
ISIC_Item == "Transportation and storage" ~ 16,
                                    ISIC_Item == "Wholesale and retail trade" ~ 17,
                                    ISIC_Item == "Food service" ~ 18,
                                    ISIC_Item == "Electricity, gas, water" ~ 19,
                                    ISIC_Item == "Health and social work" ~ 20,
                                    ISIC_Item == "Mining and quarrying" ~ 21,
                                    ISIC_Item == "Professional, scientific and technical activities" ~ 22,
                                    ISIC_Item == "Public administration" ~ 23))
    
    
# Create lists to filter countries for 2019 and time series analysis
  # 2019: N=170
  countries2019 <- AFS_ValueAdded %>% select(country, Year) %>%
    filter(Year == 2019) %>% unique() %>% select(-c("Year"))
  summary(countries2019)

  # 1995 - 2019: N = 101
  AFS_ValueAdded_CompleteCases <- AFS_ValueAdded %>%
    filter(Year %in% 1995:2019) %>%
    select(Year, country, UN_continental_region, ValueAdded_AFS_cUSD_Total) %>%
    unique() %>% filter(!(is.na(ValueAdded_AFS_cUSD_Total))) %>%
    # Limit to complete cases
      pivot_wider(names_from = Year, values_from = ValueAdded_AFS_cUSD_Total,
                  values_fill = NA) %>%
      relocate("1995", "1996", "1997", "1998", "1999", "2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019", .after = last_col()) %>%
      filter(complete.cases(.))
  completecases <- list(AFS_ValueAdded_CompleteCases$country)
  summary(completecases)

# Now load the VA per worker dataset
  VAperworker <- readRDS(file.path(data_out, "VAperworker_AFS.RDS"))
  
  # Shorten country names for visualizations
  VAperworker <- VAperworker %>%
    mutate(country = case_when(country == "United Kingdom of Great Britain and Northern Ireland" ~ "United Kingdom",
                               country == "Bolivia (Plurinational State of)" ~ "Bolivia",
                               country == "Gambia (Republic of The)" ~ "The Gambia",
                               country == "Iran (Islamic Republic of)" ~ "Iran",
                               country == "United States of America" ~ "United States",
                               country == "United Republic of Tanzania" ~ "Tanzania",
                               country == "Lao People’s Democratic Republic" ~ "Lao PDR",
                               TRUE ~ country))
    
# Create a list of countries with 2019 per worker data
  countries_2019_pw <- VAperworker %>%
    filter(!(is.na(afs_VA_perworker))) %>%
      select(c(country, Year)) %>%
      filter(Year == 2019) %>% select(c(country)) 
    summary(countries_2019_pw$country) ## 159 countries
    countries_2019_pw <- countries_2019_pw %>% pull(country)

# Now complete cases with per worker data
  completecases_df_pw <- VAperworker %>%
    filter(!(is.na(afs_VA_perworker))) %>%
    select(c(country, Year)) %>%
    mutate(count = 1) %>%
    pivot_wider(names_from = Year, values_from = count,
                      values_fill = NA) %>%
          relocate("2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019", .after = last_col()) %>%
          filter(complete.cases(.)) %>%
    select(c(country)) %>% as.data.frame()

# Create a list of the countries in complete cases for filtering time series visualizations
  completecases_pw <- completecases_df_pw %>% pull(country)

```

$~$

# Manuscript Tables and figures

### Table 1: 
This table is provided in the supplementary Excel workbook named "Classifications and Metadata.xlsx" found in the "Input Data" folder for this R project.

$~$

### Figure 1: Stability of the IO fractions over time (1995-2019)
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Set up the data
    data <- AFS_ValueAdded %>% 
      filter(!(fraction_val == 1),
             !(fraction_name == "1"),
             Year %in% 1995:2019,
             country %in% unlist(completecases)) %>%
      mutate(fraction = sub('.*_', '', fraction_name),
             fraction = case_when(fraction == "AFSManuf" ~ "Agrifood Systems Manufacturing",
                                  fraction == "HotelsRestaurants" ~ "Accommodation & Food service", 
                                  fraction == "PubAdmin" ~ "Public administration",
                                  fraction == "AccomFood" ~ "Accommodation & Food service",
                                  fraction == "ProfSciTech" ~ "Professional, scientific, & technical activities",
                                  fraction == "ElectricWater" ~ "Electricity, Gas, & Water",
                                  fraction == "WearingApparel" ~ "Wearing Apparel",
                                  fraction == "HealthSocWork" ~ "Health & Social work",
                                  fraction == "Electric" ~ "Electricity, Gas, & Water",
                                  TRUE ~ as.factor(fraction)),
             Year = as.numeric(Year),
             country = as.character(country))
    
# Create list of fractions
    fraction_list <- unique(data$fraction)

# Write a function for the regression
    regress <- function(dat) {
      model <- lm(fraction_val ~ Year + country, data = dat)
      result <-  broom::tidy(model)
      # Add 95% confidence interval to the result
          conf_int <- broom::confint_tidy(model) # you can use broom::confint() for older versions
          result <- cbind(result, conf_int)
      return(result) # exits function
    }

# Run the regression in a loop over fractions
    all_results <- data %>%
      group_by(fraction) %>%
      do(regress(.))

# Remove coefficients for country and the intercepts
    all_results <- all_results %>%
      filter(!str_detect(term, "^country")) %>%
      filter(term != "(Intercept)") %>%
      rename(pval = "p.value")
    
# Add stars for p-value
    all_results <- all_results %>%
      mutate(star = case_when(pval < 0.001 ~ "***",
                              pval >= 0.001 & pval < 0.01 ~ "**",
                              pval >= 0.01 & pval < 0.05 ~ "*",
                              pval >= 0.05 ~ "")) %>%
      select(fraction, estimate, conf.low, conf.high, star) %>%
      # create an ordering variable for the y-axis
      mutate(order_var = case_when(fraction == "Agrifood Systems Manufacturing" ~ 1,
                               fraction == "Furniture" ~ 2,
                               fraction == "Leather" ~ 3,
                               fraction == "Machinery" ~ 4,
                               fraction == "Chemicals" ~ 5,
                               fraction == "Wearing Apparel" ~ 6,
                               fraction == "Textiles" ~ 7,
                               fraction == "Rubber" ~ 8,
                               fraction == "Accommodation & Food service" ~ 9,
                               fraction == "Trade" ~ 10,
                               fraction == "Transport" ~ 11,
                               fraction == "Electricity, Gas, & Water" ~ 12,
                               fraction == "Mining" ~ 13,
                               fraction == "Professional, scientific, & technical activities" ~ 14,
                               fraction == "Health & Social work" ~ 15,
                               fraction == "Public administration" ~ 16,
                               fraction == "Rentals" ~ 17,
                               TRUE ~ NA_real_))

# Plot the estimates
    ggplot(all_results, aes(y = fct_reorder(fraction, order_var), x = estimate)) + 
      geom_point() +
      geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), width = 0.1) +
      geom_text(aes(label = star, x = conf.high), hjust = -.1) +
      scale_y_discrete(limits=rev) +
      geom_vline(xintercept = 0) +
      theme_classic() +
      labs(y = "",
           x = "Coefficient (95% Confidence Interval)",
           caption = "*** p< 0.001, ** p< 0.01, * p < 0.05") + 
      theme(plot.caption = element_text(hjust = -0.85))

# Save the plot as .png
    ggsave(file = file.path(fig_out, "ESSWP_Figure 1.png"), plot = last_plot(), width = 7, units = c("in"), dpi = 300)    
    
# Clean up
    rm(all_results, regress, data)
```

$~$

### Table 2: Adapted from Davis et al (2023)

$~$

### Figure 2: Total value added from agrifood systems, by continent - 2019
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Total value added from agrifood systems, by continent - 2019
    toplot <- AFS_ValueAdded %>% filter(Year == 2019) %>% 
      group_by(UN_continental_region, ISIC_Item, ISIC_order) %>%
      summarise(Sum_VA_AFS = sum(ValueAdded_cUSD, na.rm = TRUE)) %>%
      filter(!(is.na(UN_continental_region))) %>%
      filter(!(is.na(ISIC_Item))) %>%
      mutate(Sum_VA_AFS = case_when(is.na(Sum_VA_AFS) ~ 0,
                                     TRUE ~ Sum_VA_AFS)) %>%
      mutate(Sum_VA_AFS = Sum_VA_AFS / 1000000000) %>% # Convert to billions
      filter(!(Sum_VA_AFS == 0))
  
# Plot
    plot1 <- ggplot(toplot, aes(fill = fct_reorder(ISIC_Item, ISIC_order), y = Sum_VA_AFS, x=UN_continental_region)) + 
        geom_col() + 
      # Color palette from the alphabet palette in the pals package, added manually
      scale_fill_manual(labels = function(ISIC_Item) str_wrap(ISIC_Item, width = 30),
                        values = colors) +
      # Make the thousands separator a space per FAO formatting
      scale_y_continuous(
        labels = label_number(big.mark = " ")) +
      
      # set the left and right margins to 2 to remove unnecessary spacing in the final plot arrangement.
      theme(plot.margin = margin(6, 2, 6, 2)) +
      theme(legend.title = element_blank(),
            legend.text = element_text(size = 6),
            legend.position="none") +
      guides(fill = guide_legend(override.aes = list(size = 0.1), ncol = 4)) +
      labs(x = element_blank(), y = ("Current USD (billions)"))

    forlegend <- ggplot(toplot, aes(fill = fct_reorder(ISIC_Item, ISIC_order), y = Sum_VA_AFS, x=UN_continental_region)) + 
        geom_col() + 
      # Color palette from the alphabet palette in the pals package, added manually
      scale_fill_manual(labels = function(ISIC_Item) str_wrap(ISIC_Item, width = 30),
                        values = colors) +
      
      # set the left and right margins to 2 to remove unnecessary spacing in the final plot arrangement.
      theme(plot.margin = margin(6, 2, 6, 2)) +
      theme(legend.title = element_blank(),
            legend.text = element_text(size = 6),
            legend.position="bottom") +
      guides(fill = guide_legend(override.aes = list(size = 0.1), ncol = 4)) +
      labs(x = element_blank(), y = ("Current USD (billions)"))
    
    legend <- get_legend(forlegend)

# Now plot as shares
    toplot <- AFS_ValueAdded %>% filter(Year == 2019) %>% 
      group_by(UN_continental_region, ISIC_Item, ISIC_order) %>%
      summarise(Sum_VA_AFS = sum(ValueAdded_cUSD, na.rm = TRUE)) %>%
      filter(!(is.na(UN_continental_region))) %>%
      filter(!(is.na(ISIC_Item))) %>%
      mutate(Sum_VA_AFS = case_when(is.na(Sum_VA_AFS) ~ 0,
                                     TRUE ~ Sum_VA_AFS)) %>%
      mutate(Sum_VA_AFS = Sum_VA_AFS / 1000000000) %>% # Convert to billions
      filter(!(Sum_VA_AFS == 0)) %>%
  group_by(UN_continental_region) %>%
    mutate(cont_total = sum(Sum_VA_AFS),
           shares = (Sum_VA_AFS/cont_total)*100)
  
# Plot 
    plot2 <- ggplot(toplot, aes(fill = fct_reorder(ISIC_Item, ISIC_order), y = shares, x=UN_continental_region)) + 
        geom_col() + 
      # Color palette from the alphabet palette in the pals package, added manually
      scale_fill_manual(labels = function(ISIC_Item) str_wrap(ISIC_Item, width = 30),
                        values = colors) +
      
      # set the left and right margins to 2 to remove unnecessary spacing in the final plot arrangement.
      theme(plot.margin = margin(6, 2, 6, 2)) +
      theme(legend.title = element_blank(),
            legend.text = element_text(size = 6),
            legend.position="none") +
      guides(fill = guide_legend(override.aes = list(size = 0.1), ncol = 4)) +
      labs(x = element_blank(), y = ("Share of total agrifood systems value added (%)"))

# Combine
    plots <- plot_grid(plot1, plot2, ncol = 2, rel_widths = c(1,1))
    finalfig <- plot_grid(plots, legend, nrow = 2, rel_heights = c(2,1))

# Save the plot as .png
    ggsave(file = file.path(fig_out, "ESSWP_Figure 2.png"), plot = last_plot(), 
           width = 6.5, height = 8, units = c("in"),dpi = 300)
        
# Clean up
    rm(toplot)
```

$~$ 

### Table 2: Total value added per continent and overall in 2019
```{r, warning = FALSE, echo = FALSE, message = FALSE}
# Total value added from agrifood systems, by continent - 2019
    tabledata <- AFS_ValueAdded %>% filter(Year == 2019) %>% group_by(UN_continental_region, ISIC_Item) %>%
      summarise(Sum_VA_AFS = sum(ValueAdded_cUSD, na.rm = TRUE)) %>%
      filter(!(is.na(UN_continental_region))) %>%
      filter(!(is.na(ISIC_Item))) %>%
      mutate(Sum_VA_AFS = case_when(is.na(Sum_VA_AFS) ~ 0,
                                     TRUE ~ Sum_VA_AFS)) %>%
      mutate(Sum_VA_AFS = Sum_VA_AFS / 1000000000) %>% # Convert to billions
      pivot_wider(names_from = UN_continental_region, values_from = Sum_VA_AFS) %>%
      filter(ISIC_Item != "Other community, social and personal service activities") %>%
      rename("ISIC Category" = ISIC_Item) %>%
      mutate("Category total" = rowSums(across(where(is.numeric)), na.rm = TRUE))  

# Add continent totals
    # Create a function to sum by column
        add_totals <- function(x) x %>%
            ungroup %>% 
            bind_rows(summarise(., across(where(is.numeric), sum, na.rm = TRUE),
                                across(where(is.factor), ~ "Total")))
    
    # Append to the data frame
       tabledata <- tabledata %>% add_totals %>% 
          
    # Round everything to 2 digits
        mutate_if(is.numeric, round, 2) %>%
          
    # Replace NA with --
        mutate(across(.fns = ~ replace_na(as.character(.x), "--"))) %>%
         filter(!("ISIC Category" == "--"))
        
    # Create a table
        table <- flextable(tabledata) %>% autofit()
        
    # Save table
        save_as_docx(table, path = file.path(fig_out, "ESSWP_Table 2.docx"))
        
# Clean up
    rm(add_totals, tabledata, table)

```

$~$

### Figure 3: Share of GDP from agrifood systems by AFS sector, country level data by income group, 2019
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Share of GDP from agrifood systems by AFS sector, country, and income group, 2019
# Set up the data
    toplot <- AFS_ValueAdded %>% filter(Year == 2019) %>% 
      filter(!(is.na(VA_per_GDP))) %>% # Only show non-missing
      select(c(country, VA_per_GDP, "Income Level", VA_per_GDP_TOTAL,
               ISIC_Item, ISIC_order)) %>% 
      mutate(VA_per_GDP = round(VA_per_GDP, digits = 1)) %>%
      rename(incomelevel = "Income Level") %>%
      filter(!(is.na(incomelevel))) %>%
      mutate(incomelevel = factor(incomelevel,
                                  levels = c("Low income",
                                       "Lower middle income",
                                       "Upper middle income",
                                       "High income"))) %>%
      # Rename income levels for FAO conventions:
      mutate(incomelevel = case_when(incomelevel == "Lower middle income" ~ "Lower-middle income",
                                     incomelevel == "Upper middle income" ~ "Upper-middle income",
                                     TRUE ~ incomelevel))

# Create a separate plot for each region with every country
    # Create list of continents
        incomegroup_list <- unique(toplot$incomelevel)

    # Assign the plot code into a function
        income_plot <- function(x){
          ggplot(data = toplot %>% filter(incomelevel == x), 
                 aes(y = fct_reorder(country, VA_per_GDP_TOTAL), x = VA_per_GDP)) + 
          geom_col(aes(fill = fct_reorder(ISIC_Item, ISIC_order))) + 
          scale_fill_manual(labels = function(ISIC_Item) str_wrap(ISIC_Item, width = 30),
                            values = colors) +
          theme_classic() +
          # xlim(0,80) + # Put every income group on the same scale
          theme(plot.margin = unit(c(0.1,0.2,0.1,0.2), "cm"),
                legend.position="none",
                axis.text.x = element_text(size = 6),
                axis.text.y = element_text(size = 6)) +
          guides(fill = FALSE) +
          labs(x = "", y = "") +
          ggtitle(paste0(x)) +
          theme(plot.title = element_text(size = 8))
          }

    # Use the map function to run the plot function for every continent
        plot_list <- map(incomegroup_list, income_plot)
        
# Get the legend
    # Create the plot
        p1 <- ggplot(data = toplot %>% filter(incomelevel == "High income"), aes(y=country, x=VA_per_GDP)) + 
          geom_col(aes(fill = ISIC_Item)) + 
          scale_fill_manual(labels = function(ISIC_Item) str_wrap(ISIC_Item, width = 30),
                            values = colors) +
          theme(plot.margin = unit(c(0, 0, 0, 0), "cm")) +          
          theme_classic() +
          theme(legend.text = element_text(size = 8),
            legend.position="right") +
          guides(fill = guide_legend(title = "Sector (ISIC)", override.aes = list(size = 4),
                                 ncol = 1,
                                 keyheight = .5))

    # Get the legend
        legend <- get_legend(p1)

    # Combine the plots with the income order going from low to high
        order1 <- plot_list[[1]]
        order2 <- plot_list[[3]]
        order3 <- plot_list[[2]]
        order4 <- plot_list[[4]]
        newplotlist <- list(order1, order2, order3, order4)
        plot1 <- plot_grid(plotlist = newplotlist, nrow = 2, align = "h")
    
    # Add a single x-axis label to the bottom right
        text <- "Value added as a share of GDP (%)"
        tgrob <- ggpubr::text_grob(text, size = 8, color = "black")
        label <- as_ggplot(tgrob) + theme(plot.margin = unit(c(0, 0, 0, 0), "cm")) 
        plot2 <- plot_grid(plot1, label, nrow = 2, rel_heights = c(30,0.85))

    # Combine
        plot_grid(plot2, legend, ncol = 2, rel_widths = c(3,1), align = "vh")
        
# Save the plot as .png (because elements are overlapping in viewer)
    ggsave(file = file.path(fig_out, "ESSWP_Figure 3.png"), plot = last_plot(), width = 7.5, height = 9.5, units = c("in"), dpi = 300)
    
# Clean up
    rm(toplot, incomegroup_list, income_plot, plot_list, p1, tgrob, label, text, text2, label2, labels, plot2, legend)
```

$~$

### Figure 4: Share of GDP from agrifood systems by GDP per capita with and without primary production, Country-level average 2019
```{r, warning = FALSE, messages = FALSE, echo = TRUE}

    toplot <- AFS_ValueAdded %>% filter(Year %in% 2019) %>%
      select(c("country", "GDP_cUSD", "population", "UN_continental_region", "VA_per_GDP_TOTAL")) %>% # Remove ISIC item level columns  
      unique() %>% # De-duplicate (now that only total level data are left)
      mutate(GDP_pc = (GDP_cUSD / population) / 1000) %>% # convert to thousands per capita
      group_by(country, UN_continental_region) %>%
      filter(!(is.na(VA_per_GDP_TOTAL))) %>%
      filter(!(is.na(UN_continental_region))) %>% 
  unique() %>% filter(!(is.na(GDP_pc))) 

# Plot including primary production
    withag <- ggplot(toplot, aes(color=UN_continental_region, y=VA_per_GDP_TOTAL, x=GDP_pc)) + 
      geom_point(size = 2) + 
      # Label the points >95th percentile of value added from AFS as a share of GDP
      # geom_text(aes(label= ifelse(VA_per_GDP_TOTAL >
      #                               quantile(VA_per_GDP_TOTAL, 0.9) |
      #                               GDP_pc > quantile(GDP_pc, 0.9),
      #    as.character(country),''), vjust="inward",hjust="inward")) +
      scale_color_brewer(palette = "Set1") +
      ylim(0,100) + # allow different y-axes across plots
      theme_classic() +
      labs(x = "GDP per capita (current USD, thousands)", y = ("Value added as share of GDP (%)")) + 
      ggtitle("Including primary production") +
      theme(legend.text = element_text(size = 8),
            legend.position="none",
            axis.title.x = element_text(size = 6),
            axis.title.y = element_text(size = 6),
            plot.title = element_text(size = 8)) +
      guides(color = guide_legend(title = "Region", override.aes = list(size = 3)))
    
    toplot2 <- AFS_ValueAdded %>% filter(Year == 2019) %>%
      filter(ISIC_Item != "Agriculture, forestry and fishing") %>%
      # Recalculate the total value added from all sectors except agriculture, forestry, and fishing
      # First recalculate the value added from the non-production AFS
          group_by(country, UN_continental_region, Year, GDP, GDP_cUSD, population) %>%
          filter(!(is.na(ValueAdded_LCU))) %>%
          filter(!(is.na(UN_continental_region))) %>%
          summarise(VAperGDP_noag = (sum(ValueAdded_LCU) / GDP)*100) %>%
          mutate(GDP_pc = (GDP_cUSD / population) / 1000) %>% # convert to thousands per capita
          group_by(country, UN_continental_region) %>%
      unique() %>% filter(!(is.na(VAperGDP_noag))) %>%
      filter(!(is.na(GDP_pc)))

    
    # Plot without primary production
        withoutag <- ggplot(toplot2, aes(color=UN_continental_region, y=VAperGDP_noag, x=GDP_pc)) + 
          geom_point(size = 2) + 
          # Label the points >95th percentile of value added from AFS as a share of GDP
          # geom_text(aes(label= ifelse(VAperGDP_noag > quantile(VAperGDP_noag, 0.9) | 
          #                               GDP_pc > quantile(GDP_pc, 0.9),
          #    as.character(country),''), vjust="inward",hjust="inward")) +
          scale_color_brewer(palette = "Set1") +
          ylim(0,20) + # allow different y-axes across plots
          theme_classic() +
          labs(x = "GDP per capita (current USD, thousands)", y = ("Value added as share of GDP (%)")) + 
          ggtitle("Excluding primary production") +
          theme(legend.text = element_text(size = 8),
                legend.position="none",
                axis.title.x = element_text(size = 6),
                axis.title.y = element_text(size = 6),
                plot.title = element_text(size = 8)) +
          guides(color = guide_legend(title = "Region", override.aes = list(size = 3)))

# Get the legend
    plotforlegend <- ggplot(toplot2, aes(color=UN_continental_region, y=VAperGDP_noag, x=GDP_pc)) + 
          geom_point(size = 2) + 
          scale_color_brewer(palette = "Set1") +
          theme_classic() +
          labs(x = "GDP per capita (current USD, thousands)", y = ("Value added as share of GDP (%)")) + 
          ggtitle("Including primary production") +
          theme(legend.text = element_text(size = 8),
                legend.position="bottom",
                axis.title.x = element_text(size = 6),
                axis.title.y = element_text(size = 6),
                plot.title = element_text(size = 8)) +
          guides(color = guide_legend(title = "Region", override.aes = list(size = 3)))
    legend <- get_legend(plotforlegend)

# Combine the plots    
    plots <- cowplot::plot_grid(withag, withoutag, ncol = 2)
    combo <- plot_grid(plots, legend, nrow = 2, rel_heights = c(1,.1))
    combo
    
# Save the plot as .png
    ggsave(file = file.path(fig_out, "ESSWP_Figure 4.png"), plot = last_plot(), width = 7, units = c("in"),dpi = 300)
    
# Clean up 
    rm(combo, plots, legend, plotforlegend, withoutag, withag, toplot, toplot2)

```

$~$

### Figure 5: Top 10% outliers in terms of value added from outside primary production as a share of GDP.
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Recreate the data frame for Figure 3
    toplot2 <- AFS_ValueAdded %>% filter(Year == 2019) %>%
      filter(ISIC_Item != "Agriculture, forestry and fishing") %>%
      # Recalculate the total value added from all sectors except agriculture, forestry, and fishing
      # First recalculate the value added from the non-production AFS
          group_by(country, UN_continental_region, Year, GDP, GDP_cUSD, population) %>%
          filter(!(is.na(ValueAdded_LCU))) %>%
          filter(!(is.na(UN_continental_region))) %>%
          summarise(VAperGDP_noag = (sum(ValueAdded_LCU) / GDP)*100) %>%
          mutate(GDP_pc = (GDP_cUSD / population) / 1000) %>% # convert to thousands per capita
          group_by(country, UN_continental_region) %>%
      unique() %>% filter(!(is.na(VAperGDP_noag))) %>%
      filter(!(is.na(GDP_pc)))

      # Now filter only the outliers (top 10%)
          toplot2$pctle_90 <- quantile(toplot2$VAperGDP_noag, 0.9)
          toplot2 <- toplot2 %>% filter(VAperGDP_noag > pctle_90 & !(is.na(VAperGDP_noag)))
          
      # Now use the complete dataset with ISIC level observations and use the outlier dataset to filter out the countries. Use only 2019 otherwise some countries will have a mix of aggregate manufacturing and disaggregated categories if UNIDO data is only available for a subset of the years and the resulting figure would be misleading
          toplot3 <- AFS_ValueAdded %>%
            filter(country %in% toplot2$country,
               Year == 2019,
               ISIC_Item != "Agriculture, forestry and fishing") %>%
            filter(!(is.na(ValueAdded_LCU))) %>%
            filter(!(is.na(UN_continental_region)))
            
            # Calculate a pseudo total to sort the graph
               tots <- toplot3 %>% group_by(country) %>%
               summarise(pseudototal = sum(VA_per_GDP, na.rm = TRUE)) %>%
               ungroup()
               
               toplot3 <- left_join(toplot3, tots, by = "country")

# Create a plot showing the composition of their AFS value added
      p1 <- ggplot(data = toplot3, 
             aes(y = fct_reorder(country, pseudototal), x = VA_per_GDP)) + 
      geom_col(aes(fill = fct_reorder(ISIC_Item, ISIC_order))) + 
      scale_fill_manual(labels = function(ISIC_Item) str_wrap(ISIC_Item, width = 30),
                        values = colors) +
      theme_classic() +
      theme(plot.margin = unit(c(.5,.5,0,0), "cm"),
            legend.position="none",
            axis.text.x = element_text(size = 6),
            axis.text.y = element_text(size = 6),
            legend.text=element_text(size=6)) +
      guides(fill = FALSE) +
      labs(x = "Share of GDP (%)", y = "")
      
# Now get the legend separately
    p2 <- ggplot(data = toplot3, 
             aes(y = fct_reorder(country, pseudototal), x = VA_per_GDP)) + 
      geom_col(aes(fill = fct_reorder(ISIC_Item, ISIC_order))) + 
      scale_fill_manual(labels = function(ISIC_Item) str_wrap(ISIC_Item, width = 30),
                        values = colors) +
      theme_classic() +
      theme(plot.margin = unit(c(.5,.5,0,0), "cm"),
            legend.position="right",
            axis.text.x = element_text(size = 6),
            axis.text.y = element_text(size = 6),
            legend.text=element_text(size=6)) +
      guides(fill = guide_legend(title = "Sector (ISIC)", override.aes = list(size = 3),
                             ncol = 1,
                             keyheight = .5)) +
      labs(x = "Share of GDP (%)", y = "")
  legend <- get_legend(p2)

# Combine plot and legend
  plot_grid(p1, legend, ncol = 2, rel_widths = c(4,1))
  
# Save the plot as .png (because elements are overlapping in viewer)
    ggsave(file = file.path(fig_out, "ESSWP_Figure 5.png"), plot = last_plot(), width = 8, height = 7, units = c("in"), dpi = 300)
    
# Clean up
    rm(toplot, toplot2, legend, p1, p2)
```

$~$

### Figure 6: Value added over time, by sector, 1995-2019, limited to complete cases (N=101)
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
    toplot <- AFS_ValueAdded %>%
      mutate(Year = as.numeric(Year)) %>%
      group_by(Year, ISIC_Item, ISIC_order) %>%
      filter(ISIC_Item != "Agriculture, forestry and fishing",
             Year %in% 1995:2019,
             country %in% unlist(completecases)) %>%
      summarise(Ncountries = sum(!is.na(ValueAdded_cUSD)),
                ValueAdded_cUSD = sum(ValueAdded_cUSD, na.rm = T)) %>%
      mutate(ValueAdded_cUSD = ValueAdded_cUSD/1000000000) %>% # Convert to billions
      filter(!(ValueAdded_cUSD==0))    
  
# second data frame to label only the end of the lines
    toplot2 <- toplot %>% filter(Year == 2019)

# Plot 
    plot <- ggplot(toplot, aes(y=ValueAdded_cUSD, x=Year, fill = fct_reorder(ISIC_Item, ISIC_order))) +
      geom_col(aes(fill = fct_reorder(ISIC_Item, ISIC_order))) + 
      scale_fill_manual(labels = function(ISIC_Item) str_wrap(ISIC_Item, width = 30),
                            values = colors) +
            theme_classic() +
      # Make the thousands separator a space per FAO formatting
      scale_y_continuous(
        labels = label_number(big.mark = " ")) +
      theme(legend.position="none",
            axis.text.x = element_text(size = 6),
            axis.text.y = element_text(size = 6),
            axis.title.y = element_text(size = 8)) +
      labs(y = ("Value added from agrifood systems, current USD (billions)")) 
    
    p1 <- ggplot(toplot, aes(y=ValueAdded_cUSD, x=Year, fill = fct_reorder(ISIC_Item, ISIC_order))) +
      geom_col(aes(fill = fct_reorder(ISIC_Item, ISIC_order))) + 
      scale_fill_manual(labels = function(ISIC_Item) str_wrap(ISIC_Item, width = 30),
                            values = colors) +
            theme_classic() +
      theme(legend.text = element_text(size = 6),
            legend.position="right") +
      guides(fill = guide_legend(title = "Sector (ISIC)", override.aes = list(size = 3),
                                 ncol = 1,
                                 keyheight = .5))
    legend <- get_legend(p1)

# Combine plot and legend
    plot_grid(plot, legend, nrow = 1, rel_widths = c(3,1))

# Save the plot as .png
    ggsave(file = file.path(fig_out, "ESSWP_Figure 6.png"), plot = last_plot(), width = 7, units = c("in"),dpi = 300)    
    
# Clean up
    rm(toplot, toplot2, legend, p1, p2)
```

$~$

### Figure 7: Total value added by continent, 1995-2019, Complete cases only (N=101)
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Plot 
    toplot <- AFS_ValueAdded %>%
      filter(country %in% unlist(completecases),
             Year %in% 1995:2019) %>%
      mutate(Year = as.numeric(Year)) %>%
      group_by(Year, UN_continental_region) %>%
      summarise(ValueAdded_AFS_cUSD_Total = sum(ValueAdded_AFS_cUSD_Total, na.rm = TRUE)) %>%
      mutate(ValueAdded_AFS_cUSD_Total = ValueAdded_AFS_cUSD_Total/1000000000) # Convert to billions

    ggplot(toplot, aes(y=ValueAdded_AFS_cUSD_Total, x=Year, color = UN_continental_region)) +
        geom_line(aes(color = UN_continental_region), size = 1) + 
      scale_color_brewer(palette = "Set1") +
      # Make the thousands separator a space per FAO formatting
      scale_y_continuous(
        labels = label_number(big.mark = " ")) +
      theme_classic() +
      theme(legend.text = element_text(size = 8),
            legend.position="bottom",
            axis.text.x = element_text(size = 6),
            axis.text.y = element_text(size = 6),
            axis.title.y = element_text(size = 8)) +
      guides(color = guide_legend(title = "Region", override.aes = list(size = 3))) +
      labs(y = ("Value added from agrifood systems, current USD (billions)")) 

# Save the plot as .png
    ggsave(file = file.path(fig_out, "ESSWP_Figure 7.png"), plot = last_plot(), width = 7, units = c("in"),dpi = 300)    
    
    # The drop in the Americas from 2006-2007 is a halving of value added in the United States. The US started reporting ISIC Revision 4 in 2007. 
    
# Clean up
    rm(toplot)
```

$~$

### Table 3: VA per worker by continent
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
  Regional_Estimates <- VAperworker %>%
    filter(Year == 2019 & country %in% countries_2019_pw) %>%
    group_by(UN_continental_region) %>%
    summarise(across(4:10, sum, na.rm = TRUE)) %>%
    ungroup() %>%
    mutate(`Primary production` = ag_ValAdded/ag_emp,
           `Rest of agrifood systems` = nonag_ValAdded/nonag_afs_emp,
           `Total AFS` = AFS_ValAdded/afs_emp) %>%
    select(c(1,9:11)) %>%
    mutate(across(2:4, round, 2)) %>%
    rename(Region = UN_continental_region)

  World <- VAperworker %>% ungroup() %>%
    filter(Year == 2019 & country %in% countries_2019_pw) %>%
    select(c(4:10)) %>%
    summarise_all(sum, na.rm = TRUE) %>%
    mutate(`Primary production` = ag_ValAdded/ag_emp,
           `Rest of agrifood systems` = nonag_ValAdded/nonag_afs_emp,
           `Total AFS` = AFS_ValAdded/afs_emp) %>%
    select(c(8:10)) %>%
    mutate_all(round, 2) %>%
    mutate(Region = "World")
  
# Now create a table of VA per worker by continent, 2019
  table <- rbind(Regional_Estimates, World) %>%
    flextable() %>% autofit()
  
    # Save table
        save_as_docx(table, path = file.path(fig_out, "ESSWP_Table 3.docx"))
        
```

$~$

### Figure 8 
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
  toplot <- VAperworker %>%
    filter(Year == 2019 & country %in% countries_2019_pw) %>%
    mutate(`Primary production` = ag_ValAdded/ag_emp,
           `Rest of agrifood systems` = nonag_ValAdded/nonag_afs_emp,
           `Total AFS` = AFS_ValAdded/afs_emp) %>%
    select(c(1:3,19,25:27)) %>%
    pivot_longer(5:6, names_to = "Type", values_to = "VA_perworker") %>%
    mutate(VA_perworker = round(VA_perworker, 2)) 
  
  globalVAperworker <- ggplot(toplot, aes(y = VA_perworker, x = UN_continental_region, fill = Type)) +
    geom_boxplot() +
    scale_color_brewer(palette = "Paired") +
    scale_y_continuous(
    labels = label_number(big.mark = " ")) +
    theme_classic() +
    theme(legend.text = element_text(size = 12),
          legend.position="none") +
    labs(x = "", y = ("Value added per worker (current USD)")) 

  forlegend <- ggplot(toplot, aes(y = VA_perworker, x = UN_continental_region, fill = Type)) +
    geom_bar(position = position_stack(reverse = TRUE), stat="identity") +
    scale_color_brewer(palette = "Paired") +
    theme_classic() +
    theme(legend.text = element_text(size = 9),
          legend.position="right",
          legend.direction = "horizontal",
          legend.title = element_blank()) +
    guides(color = guide_legend(title = "", override.aes = list(size = 3))) +
    labs(x = "", y = ("Value added per worker (current USD)")) 
  
# Now workers
    toplot2 <- VAperworker %>%
      filter(Year == 2019 & country %in% countries_2019_pw) %>%
      select(c(1:3, 7:10, 19)) %>%
      rename(`Primary production` = ag_emp,
             `Rest of agrifood systems` = nonag_afs_emp) %>%
      pivot_longer(4:5, names_to = "Type", values_to = "N_workers") %>%
      mutate(N_workers = N_workers / 1000000) 

    toplot_pctTot <- VAperworker %>%
      filter(Year == 2019 & country %in% countries_2019_pw) %>%
      select(c(1:3, 16:18, 19)) %>%
      rename(`Primary production` = agemp_pctTot,
             `Rest of agrifood systems` = nonagAFS_pctTot,
             `Total AFS` = afsemp_pctTot) %>%
      group_by(UN_continental_region) %>%
      summarise(across(c(4:6), median, na.rm = TRUE)) %>%
      ungroup() %>%
      pivot_longer(2:4, names_to = "% total employment", values_to = "Median_PCT")
    
    workers <- ggplot(toplot2) +
      geom_bar(data = toplot2, aes(y = N_workers, x = UN_continental_region, fill = Type),
               position = position_stack(reverse = TRUE), stat = "identity", show.legend = FALSE) +
      scale_color_brewer(palette = "Paired") +
      scale_y_continuous("Number of workers (millions)", sec.axis = sec_axis(~ ./8.5, name = "Median percent total employment")) +
      geom_point(data = toplot_pctTot, 
                 aes(y = Median_PCT*8.5, x = UN_continental_region, shape = `% total employment`, color = `% total employment`), 
                 size = 4, show.legend = TRUE) +
      scale_shape_manual(values = c(16, 15, 17)) +
      scale_color_manual(values = c("gray", "gray40", "black")) +
      theme_classic() +
      guides(fill = "none") +
      theme(legend.text = element_text(size = 7),
            legend.position = c(0.8,.93),
            legend.direction = "vertical",
            legend.title = element_text(size = 7),
            legend.background = element_rect(fill='transparent')) +
      labs(x = "")  

# Combine plots

  legend <- cowplot::get_legend(forlegend)
  plot <- cowplot::plot_grid(globalVAperworker, workers, ncol = 2, labels = c('A', 'B'), rel_widths = c(1,1))
  cowplot::plot_grid(plot, legend, nrow = 2, rel_heights = c(10,1))
  
  # Save the plot as .png (because elements are overlapping in viewer)
    ggsave(file = file.path(fig_out, "ESSWP_Figure 8.png"), plot = last_plot(), width = 9.5, height = 7.5, units = c("in"), dpi = 300)
    
# Clean up
    rm(toplot, toplot2, globalVAperworker, workers, forlegend, legend, plot)

```

$~$

### Figure 9: VA per worker, country level data by income group, 2019
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Share of GDP from agrifood systems by AFS sector, country, and income group, 2019
# Set up the data
  toplot <- VAperworker %>%
    filter(Year == 2019 & country %in% countries_2019_pw) %>%
    select(c(1:3,14,19, 20, 24)) %>%
    rename(incomelevel = "Income Level") %>%
    filter(!(is.na(incomelevel))) %>%
    mutate(incomelevel = factor(incomelevel,
                                levels = c("Low income",
                                     "Lower middle income",
                                     "Upper middle income",
                                     "High income"))) %>%
    group_by(incomelevel) %>%
    arrange(incomelevel, desc(afs_VA_perworker)) %>%
    mutate(ordervar = 1:n()) %>%
    ungroup() %>%
    mutate(afs_VA_perworker = round(afs_VA_perworker, 2),
           PPtoRest_VApw_ratio = round(PPtoRest_VApw_ratio, 2)) %>%
  select(c(1,4,6,7,8)) %>%
  # Rename income levels for FAO conventions:
  mutate(incomelevel = case_when(incomelevel == "Lower middle income" ~ "Lower-middle income",
                               incomelevel == "Upper middle income" ~ "Upper-middle income",
                               TRUE ~ incomelevel))


  toplot2 <- VAperworker %>%
    filter(Year == 2019 & country %in% countries_2019_pw) %>%
    select(c(1:3, 12:15,19, 20, 23)) %>%
    rename(`Primary production` = ag_VA_perworker,
           `Rest of agrifood systems` = nonagAFS_VA_perworker) %>%
    rename(incomelevel = "Income Level") %>%
    filter(!(is.na(incomelevel))) %>%
    mutate(incomelevel = factor(incomelevel,
                                levels = c("Low income",
                                     "Lower middle income",
                                     "Upper middle income",
                                     "High income"))) %>%
    pivot_longer(4:5, names_to = "Type", values_to = "VA_perworker") %>%
    filter(!(is.na(VA_perworker))) %>%
    mutate(VA_perworker = round(VA_perworker, 2),
           Type = as.factor(Type)) %>%
    select(c(1,7,9,10)) %>%
  # Rename income levels for FAO conventions:
  mutate(incomelevel = case_when(incomelevel == "Lower middle income" ~ "Lower-middle income",
                               incomelevel == "Upper middle income" ~ "Upper-middle income",
                               TRUE ~ incomelevel))

# Create a separate plot for each region with every country
    # Create list of income groups
        incomegroup_list <- unique(toplot$incomelevel)
    
    # Assign the plot code into a function
        income_plot <- function(x){
          part1 <- ggplot(data = toplot %>% filter(incomelevel == x)) + 
          geom_bar(data = toplot %>% filter(incomelevel == x),
                 aes(y = forcats::fct_reorder(country, desc(ordervar)), 
                     x = afs_VA_perworker),  
                 stat = "identity",
                 fill = "gray90", 
                 show.legend = FALSE) + 
          geom_point(data = toplot2 %>% filter(incomelevel == x),
                     aes(y = country, x = VA_perworker,
                         shape = Type, color = Type), 
                     show.legend = FALSE) +
          scale_shape_manual(values = c(15, 17)) +
          # Make the thousands separator a space per FAO formatting 
          scale_x_continuous( labels = label_number(big.mark = " ")) +
          theme_classic() +
          theme(plot.margin = unit(c(0.1,0.2,0.1,0), "cm"),
                legend.position="none",
                axis.text.x = element_text(size = 5),
                axis.text.y = element_text(size = 6)) +
          guides(shape = FALSE, color = FALSE) +
          labs(x = "", y = "") +
          ggtitle(paste0(x)) +
          theme(plot.title = element_text(size = 8))
          
          part2 <- ggplot(data = toplot %>% filter(incomelevel == x)) +
            geom_text(aes(y = forcats::fct_reorder(country, desc(ordervar)), 
                     x = 1,
                     label = PPtoRest_VApw_ratio), 
                     colour = "black", size = 1.9,
                     hjust = 1) +
            scale_x_continuous(position = "top", expand = c(0,0)) +
            labs(x = "Ratio", y = "") +
            theme_classic() +
            theme(plot.margin = unit(c(0,0,0,0), "cm"),
              legend.position="none",
              axis.title.x = element_text(size = 6, hjust = 0.175),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.ticks.x=element_blank(), 
              axis.ticks.y=element_blank(),
              axis.line = element_blank())
          
          cowplot::plot_grid(part1, part2, ncol = 2, rel_widths = c(5,1),
                             align = "h")
          }
        
    # Use the map function to run the plot function for every continent
        plot_list <- map(incomegroup_list, income_plot)
        
# Get the legend
    # Create the plot
        # to fake the fill legend, add a variable:
        toplot <- toplot %>%
          mutate(fillvar = "Total Agrifood Systems",
                 fillvar = as.factor(fillvar))
        p1 <- ggplot(data = toplot %>% filter(incomelevel == "Low income")) + 
          geom_bar(data = toplot %>% filter(incomelevel == "Low income"),
                 aes(y = forcats::fct_reorder(country, desc(ordervar)), 
                     x = afs_VA_perworker, fill = fillvar),  
                 stat = "identity") + 
          geom_point(data = toplot2 %>% filter(incomelevel == "Low income"),
                     aes(y = country, x = VA_perworker,
                         shape = Type, color = Type), 
                     size = 2, show.legend = TRUE) +
          # Make the thousands separator a space per FAO formatting 
          scale_x_continuous( labels = label_number(big.mark = " ")) +
          scale_shape_manual(values = c(15, 17)) +
          scale_fill_manual("", values = c("gray90")) +
          theme_classic() +
          labs(x = "", y = "") +
          theme(plot.title = element_text(size = 8),
                plot.margin = unit(c(0,0,0,0), "cm"),
                axis.text.x = element_text(size = 6),
                axis.text.y = element_text(size = 6),
                legend.position = "right",
                legend.direction = "horizontal",
                legend.spacing = unit(0.02, "cm"),
                legend.title = element_blank()) +
          guides(fill = guide_legend(override.aes = list(size = 4, shape = NA),
                                     keyheight = .1),
                 shape = guide_legend(override.aes = list(size = 4),
                                 keyheight = .5),
                 color = guide_legend(override.aes = list(size = 4),
                                 keyheight = .5))

    # Get the legend
        legend <- cowplot::get_legend(p1)

    # Combine the plots
        plot1 <- cowplot::plot_grid(plotlist = plot_list, nrow = 2, align = "hv", rel_widths = c(1,1))
    
    # Add a single x-axis label to the bottom right
        text <- "Value added per worker (current USD)"
        tgrob <- text_grob(text, size = 8, color = "black")
        label <- as_ggplot(tgrob) + theme(plot.margin = unit(c(0, 0, 0, 0), "cm")) 
        plot2 <- cowplot::plot_grid(plot1, label, nrow = 2, rel_heights = c(30,0.85))

    # Combine
        cowplot::plot_grid(plot2, legend, ncol = 1, rel_heights = c(19,1), align = "vh")
        
# Save the plot as .png (because elements are overlapping in viewer)
    ggsave(file = file.path(fig_out, "ESSWP_Figure 9.png"), plot = last_plot(), width = 7.5, height = 9.5, units = c("in"), dpi = 300)
    
# Clean up
    rm(toplot, incomegroup_list, income_plot, plot_list, p1, tgrob, label, text, text2, label2, labels, plot2, legend)
  
```

$~$

### Figure 10: VA per worker by GDP per capita, 1995 - 2019
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Set up the data
  toplot <- VAperworker %>%
    filter(country %in% completecases_pw)

# Calculate the change in position for each country
toplot <- toplot %>%
  group_by(country) %>%
  filter(!(is.na(afs_VA_perworker))) %>%
  summarise(change = sqrt((log(GDP_percap)[which.max(Year)] - log(GDP_percap)[which.min(Year)])^2 + 
                          (log(afs_VA_perworker)[which.max(Year)] - log(afs_VA_perworker)[which.min(Year)])^2), 
            na.rm = TRUE) %>%
  right_join(toplot, by = "country")

# Determine the threshold for significant change (e.g., top 10% of changes)
threshold <- quantile(toplot$change, 0.9)

# Add a new column to differentiate significant changes
toplot <- toplot %>%
  mutate(significant = ifelse(change >= threshold, TRUE, FALSE),
         color_category = ifelse(significant, as.character(country), "gray88"))

# Filter for the latest year for each country
latest_year_data <- toplot %>%
  group_by(country) %>%
  filter(Year == max(Year)) %>%
  ungroup()

# Scatterplot with labels for significant countries
colors <- RColorBrewer::brewer.pal(n = 12, name = "Paired")
ggplot() +
  # Plot gray points first
  geom_point(data = subset(toplot, color_category == "gray88"), 
             aes(y = log(afs_VA_perworker), x = log(GDP_percap)), 
             color = "gray88") +
  geom_path(data = subset(toplot, color_category == "gray88"), 
            aes(y = log(afs_VA_perworker), x = log(GDP_percap), group = country), 
            color = "gray88") +
  # Plot colored points on top
  geom_point(data = subset(toplot, color_category != "gray88"), 
             aes(y = log(afs_VA_perworker), x = log(GDP_percap), color = color_category)) +
  geom_path(data = subset(toplot, color_category != "gray88"), 
            aes(y = log(afs_VA_perworker), x = log(GDP_percap), group = country, color = color_category)) +
  geom_text(data = subset(latest_year_data, significant == TRUE), 
            aes(y = log(afs_VA_perworker), x = log(GDP_percap), label = country), 
            hjust = 0, vjust = 0, size = 3) +  
  geom_abline(a = 0, b = 1, linetype = "dashed", color = "gray25") +
  geom_text(aes(y = 12, x = 11.67, label = "y = x"), 
            hjust = 0, vjust = 0, size = 3, color = "gray25") +
  theme(legend.position = "right",
        legend.title = element_blank(),
        legend.key.size = unit(4, "lines"),
        legend.text = element_text(size = 14)) + 
  theme_classic() +
  labs(x = "Log GDP per capita",
       y = "Log Value Added per worker in AFS") +
  scale_color_manual(values = colors) +
  theme(legend.title = element_blank())

# Save the plot as .png (because elements are overlapping in viewer)
    ggsave(file = file.path(fig_out, "ESSWP_Figure 10.png"), plot = last_plot(), width = 9.5, height = 7.5, units = c("in"), dpi = 300)

# Clean up
    rm(toplot, colors, latest_year_data, threshold)

```


# Supplementary Materials

## Appendix A: "Classifications and Metadata.xlsx" - contained in the "Input Data" folder

## Appendix B:

### Table B1 and B2: Provided in "Classifications and Metadata.xlsx"

### Table B3: Countries included in 2019 analysis
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
    # Create a table
    countries2019 <- AFS_ValueAdded %>% select(country, Year) %>%
      filter(Year == 2019) %>% unique() %>% select(-c("Year"))
    table <- flextable(countries2019) %>% autofit()
        
    # Save table
        save_as_docx(table, path = file.path(fig_out, "ESSWP_Table B3.docx"))
        
```

### Table B4: Complete cases 1995 - 2021
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Set up the data: Summarize value added to the global level by continent
    AFS_ValueAdded_CompleteCases <- AFS_ValueAdded %>%
      filter(Year %in% 1995:2019) %>%
      select(Year, country, UN_continental_region, ValueAdded_AFS_cUSD_Total) %>%
      unique() %>% filter(!(is.na(ValueAdded_AFS_cUSD_Total))) %>%
      # Limit to complete cases
        pivot_wider(names_from = Year, values_from = ValueAdded_AFS_cUSD_Total,
                    values_fill = NA) %>%
        relocate("1995", "1996", "1997", "1998", "1999", "2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019", .after = last_col()) %>%
        filter(complete.cases(.))

# Create table listing countries in the complete cases
    kable(AFS_ValueAdded_CompleteCases %>% select(country), "html", caption = "Countries with complete data from 1995-2021") %>% 
    kable_classic(full_width = F, html_font = "Cambria")
    
    # Create a table
    tabledata <- AFS_ValueAdded_CompleteCases %>% select(country)
    table <- flextable(tabledata) %>% autofit()
        
    # Save table
        save_as_docx(table, path = file.path(fig_out, "ESSWP_Table B4.docx"))
    
```

$~$

### Table B5: Countries with VA per worker, 2019
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}

data_2019 <- VAperworker %>%
  filter(!(is.na(afs_VA_perworker))) %>%
  select(c(country, Year)) %>%
  group_by(country) %>%
  mutate(From = min(Year),
         To = max(Year)) %>%
  filter(Year == From | Year == To) %>%
  select(-c(Year)) %>%
  unique() %>%
  ungroup() %>%
  rename(Country = country)
summary(data_2019$Country)
# N = 177

  # Create table listing countries and year range
    kable(data_2019, "html", caption = "Country-Years with data to calculate Value Added Per Worker") %>% 
    kable_classic(full_width = F, html_font = "Cambria")
    
  # List countries with data in 2019
    countries_2019_pw <- VAperworker %>%
    filter(!(is.na(afs_VA_perworker))) %>%
      select(c(country, Year)) %>%
      filter(Year == 2019) %>% select(c(country)) 
    summary(countries_2019_pw$country) ## 159 countries
    countries_2019_pw <- countries_2019_pw %>% pull(country)
    
    kable(countries_2019_pw, "html", caption = "Countries with data in 2019") %>% 
          kable_classic(full_width = F, html_font = "Cambria")
    
    # Create a table
    fortable2019 <- as.data.frame(countries_2019_pw)
    table <- flextable(fortable2019) %>% autofit()
        
    # Save table
        save_as_docx(table, path = file.path(fig_out, "ESSWP_Table B5.docx"))
```

$~$

### Table B6: VA per worker complete cases, 1995-2019
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
    table <- flextable(completecases_df_pw) %>% autofit()
        
    # Save table
        save_as_docx(table, path = file.path(fig_out, "ESSWP_Table B6.docx"))
        
# Clean up
  rm(table)

```

$~$

### Table B7: Number of people employed in agrifood systems, 2019, by continent
```{r, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
  summary <- VAperworker %>%
    filter(Year == 2019 & country %in% countries_2019_pw) %>%
    select(c(1:3, 7:10, 19)) %>%
    mutate(ag_emp = ag_emp / 1000000,
           nonag_afs_emp = nonag_afs_emp / 1000000) %>%
    group_by(UN_continental_region) %>%
    summarise(ag_emp = sum(ag_emp, na.rm = TRUE),
              nonag_afs_emp = sum(nonag_afs_emp, na.rm = TRUE)) %>%
    rename(`Primary production` = ag_emp,
           `Rest of agrifood systems` = nonag_afs_emp) %>%
    ungroup()
  
  summary2 <- VAperworker %>%
    filter(Year == 2019 & country %in% countries_2019_pw) %>%
    select(c(1:3, 7:10, 19)) %>%
    mutate(ag_emp = ag_emp / 1000000,
           nonag_afs_emp = nonag_afs_emp / 1000000) %>%
    ungroup() %>%
    summarise(ag_emp = sum(ag_emp, na.rm = TRUE),
              nonag_afs_emp = sum(nonag_afs_emp, na.rm = TRUE)) %>%
    rename(`Primary production` = ag_emp,
           `Rest of agrifood systems` = nonag_afs_emp) %>%
    mutate(UN_continental_region = "World") 
  employment <- rbind(summary, summary2) 
  employment$Total <- rowSums(employment[, c(2,3)])
  employment <- employment %>%
    mutate(`Primary production (% Total)` = (`Primary production`/Total)*100,
           `Rest of AFS (% Total)` = (`Rest of agrifood systems`/Total)*100) %>%
    mutate(across(2:6, ~round(., digits = 2)))
  table <- flextable(employment) %>% autofit()
        
    # Save table
        save_as_docx(table, path = file.path(fig_out, "ESSWP_Table B7.docx"))
  
  
# Clean up
  rm(summary, summary2, employment, table)
  
```

$~$

### Figure B1: Destination of primary production inputs, 2019
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Start with the IO data
  IO_data_nomargins <- readRDS(file.path(data_out, "IO_data_nomargins.rds"))

# Merge in the country name
  countries <- AFS_ValueAdded %>% select(c(ISO, country)) %>% unique()
  IO_data_nomargins <- left_join(IO_data_nomargins, countries, by = "ISO")
  IO_data_nomargins <- IO_data_nomargins %>%
    filter(!(is.na(country))) %>%
    filter(country %in% unlist(completecases))

# Relabel all the non-ag, non-food sectors to simplify
nonag <- c("Mining and Quarrying",
          "Petroleum, Chemical and Non-Metallic Mineral Products",
          "Metal Products",
          "Electrical and Machinery",
          "Transport Equipment",
          "Other Manufacturing",
          "Recycling",
          "Electricity, Gas and Water",
          "Construction",
          "Maintenance and Repair",
          "Transport",
          "Post and Telecommunications",
          "Finacial Intermediation and Business Activities",
          "Public Administration",
          "Education, Health and Other Services",
          "Private Households",
          "Others",
          "Re-export & Re-import")

# Sum the whole world up by year
  data <- IO_data_nomargins %>%
    filter(Year <= 2019) %>%
    group_by(Year, Col_Name) %>%
    mutate(From = case_when(From != "imp" ~ "Domestic production",
                            From == "imp" ~ "Imports")) %>%
    ungroup() %>%
    mutate(across(c("Row_Name", "Col_Name"), ~case_when(. %in% nonag | . %in% nonag ~ "Other", TRUE ~ .))) %>%
    aggregate(Value ~ Year + Row_Name + Col_Name, FUN = sum) 

# Keep only fisheries + agriculture inputs
  toplot <- data %>%
    filter(Row_Name %in% c("Agriculture", "Fishing")) %>%
    mutate(Row_Name = "Primary production") %>%
    aggregate(Value ~ Col_Name + Year, FUN = sum) 

# Calculate percent
  toplot <- toplot %>% 
    rename(to = Col_Name) %>%
    group_by(Year) %>%
    mutate(total = sum(Value)) %>%
    ungroup() %>%
    mutate(val_pct = Value/total,
           labels = scales::percent(val_pct %>% round(3)),
           val_pct = val_pct*100) 

# second data frame to label only the end of the lines
    toplot2 <- toplot %>% filter(Year == 2019)

# Set colors
    colors_IOsectors <- c("#005C31","forestgreen", "#08468B","#808080", "#FFFF80", "#00998F", "#2171B5","darkturquoise", "#6BAED6" )
    
# Plot 
    plot <- ggplot(toplot, aes(y=val_pct, x=Year, fill = to)) +
      geom_col(aes(fill = to)) + 
      geom_text(aes(label = if_else(Year == 2019, labels, ""), group = to), 
                position = position_stack(vjust = 0.5)) +
      scale_fill_manual(labels = function(to) str_wrap(to, width = 30),
                            values = colors_IOsectors) +
            theme_classic() +
      theme(legend.position="none",
            axis.text.x = element_text(size = 6),
            axis.text.y = element_text(size = 6),
            axis.title.y = element_text(size = 8)) +
      labs(y = ("Share of primary production consumed (%)")) 
    
    p1 <- ggplot(toplot2, aes(y=val_pct, x=Year, fill = to)) +
      geom_col(aes(fill = to)) + 
      scale_fill_manual(labels = function(to) str_wrap(to, width = 30),
                            values = colors_IOsectors) +
            theme_classic() +
      theme(legend.text = element_text(size = 10),
            legend.position="right") +
      guides(fill = guide_legend(title = "Sector (EORA)", 
                                 override.aes = list(size = 3),
                                 ncol = 1, keyheight = 0.5))
    legend <- get_legend(p1)

# Combine plot and legend
    plot_grid(plot, legend, nrow = 1, rel_widths = c(7.5,3))

# Save the plot as .png
    ggsave(file = file.path(fig_out, "ESSWP_Figure B1.png"), plot = last_plot(), width = 8, height = 5, units = c("in"),dpi = 300)    

```

$~$

### Figure B2: Source of manufacturing data
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Set up the data
    tabledata <- AFS_ValueAdded %>% 
      select(c(country, Year, manufacturing_flag)) %>%
      arrange(country, Year) %>%
      filter(!(is.na(manufacturing_flag))) %>%
      group_by(country, manufacturing_flag) %>%
      rename(Country = country) %>%
      mutate(manufacturing_flag = case_when(
        manufacturing_flag == "UNIDO Observed" ~ "UNIDO",
        TRUE ~ manufacturing_flag)) %>%
      unique() 

# Print it as a heatmap
    ggplot(tabledata, aes(y = factor(Country, levels = rev(levels(factor(Country)))), 
                          x = factor(Year), fill = manufacturing_flag)) +
      geom_tile() +
      scale_fill_brewer(palette = "Paired") +
      theme_classic() +
      theme(axis.text.x = element_text(size = 6, angle = 90, vjust = 0.5),
            axis.text.y = element_text(size = 4),
            legend.position = "bottom") +
      labs(x = "", y = "", fill = "Source of manufacturing data") 

# Save the plot as .png
    ggsave(file = file.path(fig_out, "ESSWP_Figure B2.png"), plot = last_plot(), width = 5, height = 8, units = c("in"),dpi = 300)    

# Clean up
    rm(tabledata)

```

$~$

### Figure B3: ISIC revision used by country and year
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Set up the data
    tabledata <- AFS_ValueAdded %>% 
      select(c(country, Year, ISIC_Revision)) %>%
      rename(Country = country) %>%
      unique() %>%
      # Use pivot wider then longer to fill in the missing country-years so they show in the legend of the heatmap
      pivot_wider(names_from = Year, values_from = ISIC_Revision) %>%
      pivot_longer(2:28, names_to = "Year", values_to = "ISIC_Revision")

  # Add an ISIC Revision level for no data
    levels(tabledata$ISIC_Revision) <- c(levels(tabledata$ISIC_Revision), "No Data")
    levels(tabledata$ISIC_Revision)

  # Get hex colors  
    RColorBrewer::brewer.pal(n=2, name = "Paired")
    
# Print it as a heatmap
    ggplot(tabledata, 
           aes(y = factor(Country, levels = rev(levels(factor(Country)))), 
               x = factor(Year), fill = factor(ISIC_Revision))) +
      geom_tile() +
      scale_fill_manual(values = c("#A6CEE3", "#1F78B4"),
                        na.value = c("white"),
                        labels = c("Rev 3", "Rev 4", "No data"),
                        drop = FALSE) +
      theme_classic() +
      theme(axis.text.x = element_text(size = 6, angle = 90, vjust = 0.5),
            axis.text.y = element_text(size = 4),
            legend.position = "bottom",
            legend.key=element_rect(colour="darkslategray")) +
      labs(x = "", y = "", fill = "ISIC Revision")
    
# Save the plot as .png
    ggsave(file = file.path(fig_out, "ESSWP_Figure B3.png"), plot = last_plot(), width = 5, height = 8, units = c("in"),dpi = 300)    
    
# Clean up
    rm(tabledata)
```